### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.1

\documentclass[conference]{style/IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{A methodological framework to enable the roaming agreement digitization: An NLP-based approach\\}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
The roaming procedure maintain persistent connectivity of the subscribers across different networks and geographical regions. Roaming refers to the capability for a subscriber to access the mobile services offered by the Visited Public Mobile Network (VPMN) via the Home Public Mobile Network (HPMN), when moving out of the coverage range of HPMN [1]. However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members [2]. Reference [3] provides a list of the most commonly used GSMA standards, which can be summarized into: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 constitutes an addendum to the international RA in order to determine specific properties such as charging, billing, and accounting for a specific scenario like the SMS interworking.

While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly [4]. Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the standard templates to determine whether:

\begin{enumerate}
\item Leave an article/sub-article as found in the template thereby establishing a standard clause.

\item Introduce certain variations in the articles/sub-articles, by changing variables, e.g., MNO, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA templates.

\item Introduce completely new articles/sub-articles that respond to particular interests by constituting customized texts.

\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others

\end{enumerate}

However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e. the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange. Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations. For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text of the RA. The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text.

The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitization of Roaming Agreement and existing NLP-based digitization mechanisms as part of the related work. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 6 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 7.

\section{Related work}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{images/fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}

\end{document}

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.2

@@
 The roaming procedure maintain persistent connectivity of the subscribers across different networks and geographical regions.
-Roaming refers to the capability for a subscriber to access the mobile services offered by the Visited Public Mobile Network (VPMN) via the Home Public Mobile Network (HPMN), when moving out of the coverage range of HPMN [1].
+Roaming refers to the capability for a subscriber to access the mobile services offered by the Visited Public Mobile Network (VPMN) via the Home Public Mobile Network (HPMN), when moving out of the coverage range of HPMN \cite{b1}.
 However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
 
-In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members [2].
-Reference [3] provides a list of the most commonly used GSMA standards, which can be summarized into: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 constitutes an addendum to the international RA in order to determine specific properties such as charging, billing, and accounting for a specific scenario like the SMS interworking.
+In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}.
+Reference \cite{b3} provides a list of the most commonly used GSMA standards, which can be summarized into: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 constitutes an addendum to the international RA in order to determine specific properties such as charging, billing, and accounting for a specific scenario like the SMS interworking.
 
-While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly [4].
+While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{b4}.
 Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
@@
 
-\subsection{Maintaining the Integrity of the Specifications}
+Both in the scientific literature and in business environments there are important approaches to RA digitalization.
+Thus, the reference \cite{b5} proposes a dynamic RA between the Local 5G Operator and the MNO.
+The interaction between the two entities takes place through an Ethereum based platform.
+A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{b6}.
+This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
+The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{b7}.
+However, these contributions are focused from a RA implementation perspective rather than the negotiation context of drafting the RA.
+Similarly, the scientific literature addresses text processing systems based on nlp techniques in domains such as healthcare and the judiciary.
+Thus, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
+NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.
+In addition, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
+This linguistic analysis attempts to find the appropriate meaning of terms within a document.
+Finally, authors of reference \cite{b10} propose a model for implementing sentimental analysis using Amazon Comprehend.
+This system performs an audio-to-text transcription and then performs the processing of the obtained text.
+Although these studies are part of related work, for example, by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of negotiating the RA drafting.
+Therefore, we can affirm that our work represents a topic with a high degree of novelty.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\section{Designed Methodology}
+Before you begin to format your paper, first write and save the content as a
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\subsection{Amazon comprehend}\label{AA}
+Define abbreviations and acronyms the first time they are used in the text
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\subsection{Smilarity Analysis}
+Define abbreviations and acronyms the first time they are used in the text
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\section{Implemented System}
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\section{Discussion of Results}
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{images/fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
+\section{Conclusions}
 
 \section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
+This research was funded by Linux Foundation Mentorship Program through the project: “The Use of NLP and DLT to Enable the Digitalization of Telecom Roaming Agreements” with project identifier d8a154c6-41fb-4733-b3c8-df37796e7fa3.
 
 \begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+\bibitem{b1} I. Tanaka, "Volte roaming and interconnection standard technology", NTT Docomo Technical Journal, vol. 15, no. 2, pp. 37-41, 2013.
+\bibitem{b2} Ferwerda, R.; Bayings, M.; Van der Kam, M.; Bekkers, R.
+Advancing E-Roaming in Europe: Towards a Single “Language” for the European Charging Infrastructure.
+World Electr.
+Veh.
 J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+2018, 9, 50.
+https://doi.org/10.3390/wevj9040050.
+\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017.
+\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017.
+\bibitem{b5} N.
+Weerasinghe, T.
+Hewa, M.
+Dissanayake, M.
+Ylianttila and M.
+Liyanage, "Blockchain-based Roaming and Offload Service Platform for Local 5G Operators," 2021 IEEE 18th Annual Consumer Communications and Networking Conference (CCNC), 2021, pp.
+1-6, doi: 10.1109/CCNC49032.2021.9369516.
+\bibitem{b6} C.
+Harris, "Improving Telecom Industry Processes Using Ordered Transactions in Hyperledger Fabric," 2019 IEEE Globecom Workshops (GC Wkshps), 2019, pp.
+1-6, doi: 10.1109/GCWkshps45667.2019.9024541.
+\bibitem{b7} M.
+Huillet, "Telefónica, Deutsche Telekom and Vodafone Use Blockchain for Roaming Settlement," 2020.
+[Online].
+Available: https://cointelegraph.com/news/telefonica-deutsche-telekom-and-vodafone-use-blockchain-for-roaming-settlement.
+[Accessed: 24-Ago-2021].
+\bibitem{b8} M.
+B.C., A.
+K., M.
+Y.
+M., R.
+L.R.
+and S.
+S.R., "Intelligent Automated Text Processing System - An NLP Based Approach," 2020 5th International Conference on Communication and Electronics Systems (ICCES), 2020, pp.
+1026-1030, doi: 10.1109/ICCES48766.2020.9138070.
+\bibitem{b9} M.
+A.
+Islam and M.
+Jahidul Haque, "Evaluating Document Analysis with kNN Based Approaches in Judicial Offices of Bangladesh," 2018 Second International Conference on Computing Methodologies and Communication (ICCMC), 2018, pp.
+646-650, doi: 10.1109/ICCMC.2018.8487847.
+\bibitem{b10} G.
+Satyanarayana, J.
+Bhuvana and M.
+Balamurugan, "Sentimental Analysis on voice using AWS Comprehend," 2020 International Conference on Computer Communication and Informatics (ICCCI), 2020, pp.
+1-4, doi: 10.1109/ICCCI48352.2020.9104105.
 \end{thebibliography}

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.3

@@
 \section{Introduction}
-The roaming procedure maintain persistent connectivity of the subscribers across different networks and geographical regions.
-Roaming refers to the capability for a subscriber to access the mobile services offered by the Visited Public Mobile Network (VPMN) via the Home Public Mobile Network (HPMN), when moving out of the coverage range of HPMN \cite{b1}.
+The roaming service maintains the persistent connectivity of subscribers in different networks and locations.
+Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{b1}.
 However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
@@
 In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}.
-Reference \cite{b3} provides a list of the most commonly used GSMA standards, which can be summarized into: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 constitutes an addendum to the international RA in order to determine specific properties such as charging, billing, and accounting for a specific scenario like the SMS interworking.
+Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 is an addendum to the international RA to determine specific properties such as charging, billing and accounting for a specific scenario such as SMS interworking.
+Thus, the contractual relationship between MNOs depends on the drafting of an RA between the parties.
 
@@
 Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
-Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the standard templates to determine whether:
+Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates to determine whether:
 
 \begin{enumerate}
+\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others.
+
 \item Leave an article/sub-article as found in the template thereby establishing a standard clause.
@@
 
-\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others
-
 \end{enumerate}
@@
 Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations.
-For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text of the RA.
+For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process.
 The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text.
+For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as Amazon Comprehend and on the other hand, a comprehensive comparison between texts is established based on similarity determination techniques.
+Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitization of roaming agreements.
 
@@
 The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{b7}.
-However, these contributions are focused from a RA implementation perspective rather than the negotiation context of drafting the RA.
-Similarly, the scientific literature addresses text processing systems based on nlp techniques in domains such as healthcare and the judiciary.
-Thus, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
+However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.
+
+Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary.
+Thus, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
+This linguistic analysis attempts to find the appropriate meaning of terms within a document.
+In addition, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
 NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.
-In addition, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
-This linguistic analysis attempts to find the appropriate meaning of terms within a document.
 Finally, authors of reference \cite{b10} propose a model for implementing sentimental analysis using Amazon Comprehend.
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
-Although these studies are part of related work, for example, by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of negotiating the RA drafting.
-Therefore, we can affirm that our work represents a topic with a high degree of novelty.
+Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitization of the roaming agreement.
+Therefore, we can affirm that our work introduces a topic with a high degree of novelty.
 

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.4

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
-
 \title{A methodological framework to enable the roaming agreement digitization: An NLP-based approach\\}
@@
 \section{Implemented System}
+Define abbreviations and acronyms the first time they are used in the text
 
 \section{Discussion of Results}
+Define abbreviations and acronyms the first time they are used in the text
 
 \section{Conclusions}
-
-\section*{Acknowledgment}
-This research was funded by Linux Foundation Mentorship Program through the project: “The Use of NLP and DLT to Enable the Digitalization of Telecom Roaming Agreements” with project identifier d8a154c6-41fb-4733-b3c8-df37796e7fa3.
+Define abbreviations and acronyms the first time they are used in the text
 
 \begin{thebibliography}{00}
+
     \bibitem{b1} I. Tanaka, "Volte roaming and interconnection standard technology", NTT Docomo Technical Journal, vol. 15, no. 2, pp. 37-41, 2013.
+
 \bibitem{b2} Ferwerda, R.; Bayings, M.; Van der Kam, M.; Bekkers, R.
@@
 https://doi.org/10.3390/wevj9040050.
+
 \bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017.
+
 \bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017.
+
 \bibitem{b5} N.
@@
 1-6, doi: 10.1109/CCNC49032.2021.9369516.
+
 \bibitem{b6} C.
@@
 1-6, doi: 10.1109/GCWkshps45667.2019.9024541.
+
 \bibitem{b7} M.
@@
 [Accessed: 24-Ago-2021].
+
 \bibitem{b8} M.
@@
 1026-1030, doi: 10.1109/ICCES48766.2020.9138070.
+
 \bibitem{b9} M.
@@
 646-650, doi: 10.1109/ICCMC.2018.8487847.
+
 \bibitem{b10} G.
@@
 1-4, doi: 10.1109/ICCCI48352.2020.9104105.
+
 \end{thebibliography}
+
 \vspace{12pt}

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.5

@@
 \begin{enumerate}
-\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others.
+\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of entities, amounts and others.
 
-\item Leave an article/sub-article as found in the template thereby establishing a standard clause.
+\item Leave an article/sub-article as found in the template thereby establishing a \textit{standard clause}.
 
-\item Introduce certain variations in the articles/sub-articles, by changing variables, e.g., MNO, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA templates.
+\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA templates.
 
-\item Introduce completely new articles/sub-articles that respond to particular interests by constituting customized texts.
+\item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.
 
@@
 The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text.
-For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as Amazon Comprehend and on the other hand, a comprehensive comparison between texts is established based on similarity determination techniques.
+For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as \textit{Amazon Comprehend} and on the other hand, a comprehensive comparison between texts is established based on \textit{similarity} determination techniques.
 Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitization of roaming agreements.
@@
 
-\section{Designed Methodology}
-Before you begin to format your paper, first write and save the content as a
+\section{NLP Engine methodology}
+Overall, the logic designed for the NLP engine follows two approaches: detection and comparison.
+Detection represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement.
+Comparison represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
+For example, while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
+Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the name of the MNO and the start date of the agreement.
+The technologies that enable both detection and comparison are discussed below as part of the \textit{background}.
 
@@
 
-\subsection{Smilarity Analysis}
+\subsection{Similarity Analysis}
+Define abbreviations and acronyms the first time they are used in the text
+
+\subsection{Designed Methodology}
 Define abbreviations and acronyms the first time they are used in the text

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.6

@@
 In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}.
-Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 is an addendum to the international RA to determine specific properties such as charging, billing and accounting for a specific scenario such as SMS interworking.
-Thus, the contractual relationship between MNOs depends on the drafting of an RA between the parties.
+Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
@@
 The technologies that enable both detection and comparison are discussed below as part of the \textit{background}.
+The third section integrates these tools as part of the designed methodology.
 
-\subsection{Amazon comprehend}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text
+\subsection{Amazon comprehend}
+In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{b11}.
+The capabilities that \textit{Amazon Comprehend} integrates are key to the \textit{detection} approach.
 
 \subsection{Similarity Analysis}
-Define abbreviations and acronyms the first time they are used in the text
+Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{b12}.
+Therefore, the similarity falls within the comparison approach.
+In this regard, our work distinguishes between two types of similarities: Jaccard similarity and Cosine similarity \cite{b13}.
+While the first one is established as the size of the intersection divided by the size of the union of two sets, the second one implies the determination of the cosine of the angle between two vectors.
 
@@
 
-\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017.
+\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/the-roaming-agreement/. [Accessed: 24-Ago-2021].
 
-\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017.
+\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/roaming-hubbing/. [Accessed: 24-Ago-2021].
 
@@
 
+\bibitem{b11} AWS, “Amazon Comprehend Developer Guide,” 2021. [Online]. Available: https://docs.aws.amazon.com/comprehend/latest/dg/comprehend-dg.pdf. [Accessed: 24-Jul-2021].
+
+\bibitem{b12} J.
+Santisteban and J.
+Tejada-Cárcamo, "Unilateral Weighted Jaccard Coefficient for NLP," 2015 Fourteenth Mexican International Conference on Artificial Intelligence (MICAI), 2015, pp.
+14-20, doi: 10.1109/MICAI.2015.9.
+
+ \bibitem{b13} S.
+Gupta, “Overview of Text Similarity Metrics in Python,” May 15, 2018, 2018.
+[Online].
+Available: https://towardsdatascience.com/overview-of-text-similarity-metrics-3397c4601f50.
+[Accessed: 25-Jul-2021].
+
 \end{thebibliography}

### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.7

@@
 \subsection{Designed Methodology}
-Define abbreviations and acronyms the first time they are used in the text
+Define abbreviations and acronyms the first time they are used in the text.
 
 \section{Implemented System}
-Define abbreviations and acronyms the first time they are used in the text
+The Fig.~\ref{fig1} shows a overall architecture of the NLP Engine that integrates over a docker infrastructure, establishing as inputs the Roaming Agreement text file, as well as the GSMA standard templates; as processing layer the logic associated to the NLP Engine and as output the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations} depending of the \textit{variables} detection.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.25\textwidth]{images/NLP_Engine.png}}
+\caption{NLP Engine overall architecture.}
+\label{fig1}
+\end{figure}
+
+La primera consideración entorno a la arquitectura desarrollada radica en que el motor NLP se ha desarrollado como un Software Development Kit y por consiguiente este debe ser descagado y ejecutado desde un entrypoint.
+
+En lo relativo a la implementación de la similaridad de Jaccard y a la similaridad del coseno.
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
26.08.21.1

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+%\usepackage{biblatex}
+%\addbibresource{references/references.bib}
 
@@
 
-La primera consideración entorno a la arquitectura desarrollada radica en que el motor NLP se ha desarrollado como un Software Development Kit y por consiguiente este debe ser descagado y ejecutado desde un entrypoint.
-
-En lo relativo a la implementación de la similaridad de Jaccard y a la similaridad del coseno.
+The first consideration regarding the developed architecture is that the NLP engine has been developed as a Software Development Kit and therefore it must be downloaded and executed from an entry point.
 
@@
 Define abbreviations and acronyms the first time they are used in the text
+
+%\printbibliography
+
+%\cite{erwerda2018}
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
26.08.21.2

@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
-%\usepackage{biblatex}
-%\addbibresource{references/references.bib}
+\usepackage[sorting=none]{biblatex}
+\addbibresource{references/references.bib}
 
@@
 The roaming service maintains the persistent connectivity of subscribers in different networks and locations.
-Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{b1}.
+Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}.
 However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
 
-In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}.
-Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
+In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
+Reference \cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
-While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{b4}.
+While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}.
 Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
@@
 
-Both in the scientific literature and in business environments there are important approaches to RA digitalization.
-Thus, the reference \cite{b5} proposes a dynamic RA between the Local 5G Operator and the MNO.
+Both in the scientific literature and in business environments there are important approaches to RA digitization.
+Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO.
 The interaction between the two entities takes place through an Ethereum based platform.
-A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{b6}.
+A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.
 This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
-The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{b7}.
+The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
 However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.
@@
 Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary.
-Thus, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
+Thus, the reference \cite{8487847} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
 This linguistic analysis attempts to find the appropriate meaning of terms within a document.
-In addition, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
+In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
 NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.
-Finally, authors of reference \cite{b10} propose a model for implementing sentimental analysis using Amazon Comprehend.
+Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend.
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
@@
 \subsection{Amazon comprehend}
-In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{b11}.
+In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
 The capabilities that \textit{Amazon Comprehend} integrates are key to the \textit{detection} approach.
@@
 \subsection{Similarity Analysis}
-Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{b12}.
+Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}.
 Therefore, the similarity falls within the comparison approach.
-In this regard, our work distinguishes between two types of similarities: Jaccard similarity and Cosine similarity \cite{b13}.
+In this regard, our work distinguishes between two types of similarities: Jaccard similarity and Cosine similarity \cite{Gupta2018}.
 While the first one is established as the size of the intersection divided by the size of the union of two sets, the second one implies the determination of the cosine of the angle between two vectors.
@@
 
-%\printbibliography
-
-%\cite{erwerda2018}
-
-\begin{thebibliography}{00}
-
-\bibitem{b1} I. Tanaka, "Volte roaming and interconnection standard technology", NTT Docomo Technical Journal, vol. 15, no. 2, pp. 37-41, 2013.
-
-\bibitem{b2} Ferwerda, R.; Bayings, M.; Van der Kam, M.; Bekkers, R.
-Advancing E-Roaming in Europe: Towards a Single “Language” for the European Charging Infrastructure.
-World Electr.
-Veh.
-J.
-2018, 9, 50.
-https://doi.org/10.3390/wevj9040050.
-
-\bibitem{b3} ROCCO, “The International Roaming Agreement,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/the-roaming-agreement/. [Accessed: 24-Ago-2021].
-
-\bibitem{b4} ROCCO, “What is ROAMING HUBBING?,” 2017. [Online]. Available: https://www.roccoresearch.com/portfolio-items/roaming-hubbing/. [Accessed: 24-Ago-2021].
-
-\bibitem{b5} N.
-Weerasinghe, T.
-Hewa, M.
-Dissanayake, M.
-Ylianttila and M.
-Liyanage, "Blockchain-based Roaming and Offload Service Platform for Local 5G Operators," 2021 IEEE 18th Annual Consumer Communications and Networking Conference (CCNC), 2021, pp.
-1-6, doi: 10.1109/CCNC49032.2021.9369516.
-
-\bibitem{b6} C.
-Harris, "Improving Telecom Industry Processes Using Ordered Transactions in Hyperledger Fabric," 2019 IEEE Globecom Workshops (GC Wkshps), 2019, pp.
-1-6, doi: 10.1109/GCWkshps45667.2019.9024541.
-
-\bibitem{b7} M.
-Huillet, "Telefónica, Deutsche Telekom and Vodafone Use Blockchain for Roaming Settlement," 2020.
-[Online].
-Available: https://cointelegraph.com/news/telefonica-deutsche-telekom-and-vodafone-use-blockchain-for-roaming-settlement.
-[Accessed: 24-Ago-2021].
-
-\bibitem{b8} M.
-B.C., A.
-K., M.
-Y.
-M., R.
-L.R.
-and S.
-S.R., "Intelligent Automated Text Processing System - An NLP Based Approach," 2020 5th International Conference on Communication and Electronics Systems (ICCES), 2020, pp.
-1026-1030, doi: 10.1109/ICCES48766.2020.9138070.
-
-\bibitem{b9} M.
-A.
-Islam and M.
-Jahidul Haque, "Evaluating Document Analysis with kNN Based Approaches in Judicial Offices of Bangladesh," 2018 Second International Conference on Computing Methodologies and Communication (ICCMC), 2018, pp.
-646-650, doi: 10.1109/ICCMC.2018.8487847.
-
-\bibitem{b10} G.
-Satyanarayana, J.
-Bhuvana and M.
-Balamurugan, "Sentimental Analysis on voice using AWS Comprehend," 2020 International Conference on Computer Communication and Informatics (ICCCI), 2020, pp.
-1-4, doi: 10.1109/ICCCI48352.2020.9104105.
-
-\bibitem{b11} AWS, “Amazon Comprehend Developer Guide,” 2021. [Online]. Available: https://docs.aws.amazon.com/comprehend/latest/dg/comprehend-dg.pdf. [Accessed: 24-Jul-2021].
-
-\bibitem{b12} J.
-Santisteban and J.
-Tejada-Cárcamo, "Unilateral Weighted Jaccard Coefficient for NLP," 2015 Fourteenth Mexican International Conference on Artificial Intelligence (MICAI), 2015, pp.
-14-20, doi: 10.1109/MICAI.2015.9.
-
-\bibitem{b13} S.
-Gupta, “Overview of Text Similarity Metrics in Python,” May 15, 2018, 2018.
-[Online].
-Available: https://towardsdatascience.com/overview-of-text-similarity-metrics-3397c4601f50.
-[Accessed: 25-Jul-2021].
-
-\end{thebibliography}
+\printbibliography
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
26.08.21.5

--- 2021-08-26 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
@@
 \section{Discussion of Results}
-Define abbreviations and acronyms the first time they are used in the text
+Since PDF, i.e., input files of the NLP Engine consist of unstructured text and e.g., undesired characters may remain despite parsing of the text, it is mandatory determine the \textit{accuracy} of the results obtained once the file with the classification of articles/sub-articles has been populated.
+For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results.
+On the one hand, a verification based on human eye inspection and on the other hand, a verification based on symbol comparison.
+The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange.
+The experiments conducted to determine the accuracy are described below, while the results obtained are analyzed.
+
+\subsection{Accuracy determination based on human eye inspection}
+The first accuracy analysis involves randomly selecting 5 articles from each of the sample Roaming Agreements and performing a visual inspection (human-eye inspection) to determine the number of variables, variations, standard clauses and custom texts that exist.
+The results obtained are then compared with the values populated in the article and sub-article classification file for the same articles.
+Considering that the results obtained from the visual inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, the confusion matrices obtained are as follows:
+
+\subsection{Accuracy determination based on symbol comparison}
+The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
+For that purpose, the text comparison tool [Countwordsfree](https://countwordsfree.comcomparetexts) has been used manually copying sub-article by sub-article.
+For each sub-article is determined:
+ \begin{enumerate}
+\item Common percentage of words between compared sub-articles.
+\item Difference percentage of words between compared sub-articles.
+\item Common words between compared sub-articles.
+\item Difference words between compared sub-articles.
+\end{enumerate}
+
+Considering that for each sub-article the characters that determine the differences have been analyzed, determining that they are mostly end-of-line characters, quotation marks, parentheses and brackets, the threshold of the common percentage of words is determined as the worst case, i.e., where a greater combination of these characters appears.
+From the threshold, the rest of the cases found with lower common percentage of words will be considered failures.
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
26.08.21.6

@@
 \begin{document}
-\title{A methodological framework to enable the roaming agreement digitization: An NLP-based approach\\}
+\title{A methodological framework to enable the roaming agreement digitalization: An NLP-based approach\\}
 
@@
 the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange.
-Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations.
+Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitalization system for RA drafting negotiations.
 For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process.
@@
 For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as \textit{Amazon Comprehend} and on the other hand, a comprehensive comparison between texts is established based on \textit{similarity} determination techniques.
-Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitization of roaming agreements.
+Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitalization of roaming agreements.
 
-The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitization of Roaming Agreement and existing NLP-based digitization mechanisms as part of the related work.
+The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitalization of Roaming Agreement and existing NLP-based digitalization mechanisms as part of the related work.
 Section 3 establishes the designed methodology.
@@
 
-Both in the scientific literature and in business environments there are important approaches to RA digitization.
+Both in the scientific literature and in business environments there are important approaches to RA digitalization.
 Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO.
@@
 A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.
-This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
+This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitalization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
 The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
@@
 Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary.
-Thus, the reference \cite{8487847} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
+Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
 This linguistic analysis attempts to find the appropriate meaning of terms within a document.
@@
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
-Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitization of the roaming agreement.
+Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitalization of the roaming agreement.
 Therefore, we can affirm that our work introduces a topic with a high degree of novelty.
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.25\textwidth]{images/NLP_Engine.png}}
+\centerline{\includegraphics[width=0.2\textwidth]{images/NLP_Engine.png}}
 \caption{NLP Engine overall architecture.}
@@
 The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
-For that purpose, the text comparison tool [Countwordsfree](https://countwordsfree.comcomparetexts) has been used manually copying sub-article by sub-article.
+For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) has been used manually copying sub-article by sub-article.
 For each sub-article is determined:
@@
 \section{Conclusions}
-Define abbreviations and acronyms the first time they are used in the text
+Considering that the proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems, as well as the integration of the NLP Engine part.
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
26.08.21.8

@@
 In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
-Reference \cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
+Reference \cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
@@
 
-\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA templates.
+\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA standard templates.
 
@@
 However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e.
-the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange.
+the MNOs, still use asynchronous flows such as email or even regular mail for information exchange.
 Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitalization system for RA drafting negotiations.
-For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process.
-The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text.
-For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as \textit{Amazon Comprehend} and on the other hand, a comprehensive comparison between texts is established based on \textit{similarity} determination techniques.
-Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitalization of roaming agreements.
+For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a digitization process of negotiation procedures for a transparent drafting of Roaming Agreements.
+The NLP engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
+For this purpose, the NLP engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
+The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool.
+This article includes not only the design phase, but also the implementation and evaluation of the tool.
 
-The rest of this manuscript is structured as follows: Section 2 reviews both attempts at a transparent digitalization of Roaming Agreement and existing NLP-based digitalization mechanisms as part of the related work.
+The rest of this manuscript is structured as follows: Section 2 reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems as part of related work.
 Section 3 establishes the designed methodology.
 The implementation of our system are described in Section 4.
-Section 6 discusses the results of conducted experiments.
-Finally, the conclusions of the manuscript are included in Section 7.
+Section 5 discusses the results of conducted experiments.
+Finally, the conclusions of the manuscript are included in Section 6.
 
@@
 The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
-However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.
+Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.
 
 Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary.
-Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
+Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
 This linguistic analysis attempts to find the appropriate meaning of terms within a document.
@@
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
-Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitalization of the roaming agreement.
+Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement.
 Therefore, we can affirm that our work introduces a topic with a high degree of novelty.
@@
 \section{NLP Engine methodology}
-Overall, the logic designed for the NLP engine follows two approaches: detection and comparison.
-Detection represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement.
-Comparison represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
+Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}.
+While \textit{detection} has words as its basic processing unit, \textit{comparison} has sub-articles as its basic processing unit.
+\textit{Detection} represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement.
+\textit{Comparison} represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
 For example, while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
-Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the name of the MNO and the start date of the agreement.
-The technologies that enable both detection and comparison are discussed below as part of the \textit{background}.
-The third section integrates these tools as part of the designed methodology.
+Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial name of a MNO and the start date of the agreement.
+The technologies that enable both \textit{detection} and \textit{comparison} are discussed below as part of the \textit{background}.
+The third section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.
 
@@
 In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
-The capabilities that \textit{Amazon Comprehend} integrates are key to the \textit{detection} approach.
+The capabilities that \textit{Amazon Comprehend} integrates are key in the \textit{detection} approach.
 
@@
 \section{Implemented System}
-The Fig.~\ref{fig1} shows a overall architecture of the NLP Engine that integrates over a docker infrastructure, establishing as inputs the Roaming Agreement text file, as well as the GSMA standard templates; as processing layer the logic associated to the NLP Engine and as output the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations} depending of the \textit{variables} detection.
+The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure, which establishes as inputs the Roaming Agreement text file, as well as the GSMA standard templates; as processing layer the logic associated to the NLP Engine and as output the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations} depending of the \textit{variables} detection.
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
26.08.21.2

@@
 \section{Implemented System}
-The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure, which establishes as inputs the Roaming Agreement text file, as well as the GSMA standard templates; as processing layer the logic associated to the NLP Engine and as output the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations} depending of the \textit{variables} detection.
+The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts.
+First, the input files include the Roaming Agreement text file as well as the GSMA standard templates.
+The processing layer includes the logic associated with the NLP engine, i.e.
+the implementation of the designed methodology.
+The output file constitutes a JSON file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
+Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.2\textwidth]{images/NLP_Engine.png}}
+\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
 \caption{NLP Engine overall architecture.}
@@
 
-The first consideration regarding the developed architecture is that the NLP engine has been developed as a Software Development Kit and therefore it must be downloaded and executed from an entry point.
+Regarding the input and output files, these are associated to the container through volumes.
+In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point.
+Although the NLP Engine constitutes a library, it must in turn integrate other libraries, among which boto3 \cite{boto3}.
+Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS).
+The NLP Engine imports the service associated to Amazon Comprehend.
+Other library imported into NLP Engine library is PyMuPDF (\cite{PyMuPDF}), which is used by the NLP Engine to extract headers and footers from the PDF files.
+Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports.
 

### 2021-08-26 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.1

@@
 the implementation of the designed methodology.
-The output file constitutes a JSON file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
+The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
 Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.
@@
 \section{Discussion of Results}
-Since PDF, i.e., input files of the NLP Engine consist of unstructured text and e.g., undesired characters may remain despite parsing of the text, it is mandatory determine the \textit{accuracy} of the results obtained once the file with the classification of articles/sub-articles has been populated.
+Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated.
 For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results.
-On the one hand, a verification based on human eye inspection and on the other hand, a verification based on symbol comparison.
-The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange.
-The experiments conducted to determine the accuracy are described below, while the results obtained are analyzed.
+On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison.
+The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}.
+Each experiment is described below and the results obtained are discussed in the same section.
 
-\subsection{Accuracy determination based on human eye inspection}
-The first accuracy analysis involves randomly selecting 5 articles from each of the sample Roaming Agreements and performing a visual inspection (human-eye inspection) to determine the number of variables, variations, standard clauses and custom texts that exist.
-The results obtained are then compared with the values populated in the article and sub-article classification file for the same articles.
-Considering that the results obtained from the visual inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, the confusion matrices obtained are as follows:
+\subsection{Accuracy determination based on a simple inspection at sub-article level}
+The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a variation, a standard clause or a customized text with respect to the GSMA standard template.
+Additionally, the detected variables are analyzed.
+The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles.
+Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text:
+\begin{enumerate}
+\item True Positive is when the item is observed and predicted.
+\item True Negative is when the item is observed but not predicted.
+\item False Positive is when the item is not observed but still predicted.
+\item False Negative is when the item is neither observed nor predicted..
+\end{enumerate}
+
+The following confusion matrices allow us to analyze the results for each roaming agreement:
 
@@
 The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
-For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) has been used manually copying sub-article by sub-article.
+For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) is used manually copying sub-article by sub-article.
 For each sub-article is determined:
+
  \begin{enumerate}
@@
 
-Considering that for each sub-article the characters that determine the differences have been analyzed, determining that they are mostly end-of-line characters, quotation marks, parentheses and brackets, the threshold of the common percentage of words is determined as the worst case, i.e., where a greater combination of these characters appears.
-From the threshold, the rest of the cases found with lower common percentage of words will be considered failures.
+The following radar plots allow us to analyze the results for each roaming agreement:
 

### 2021-08-27 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.2

@@
 This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
 or Math in Paper Title or Abstract.
@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+NLP, Roaming Agreement, Amazon Comprehend, Similarity
 \end{IEEEkeywords}
@@
 \subsection{Designed Methodology}
-Define abbreviations and acronyms the first time they are used in the text.
+The flow chart in Fig.~\ref{fig1} is a general scheme of the methodology designed for the NLP Engine, which will be explained in detail below.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
+\caption{Overview of the designed methodology.}
+\label{fig1}
+\end{figure}
 
 \section{Implemented System}
-The Fig.~\ref{fig1} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts.
+The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts.
 First, the input files include the Roaming Agreement text file as well as the GSMA standard templates.
@@
 \caption{NLP Engine overall architecture.}
-\label{fig1}
+\label{fig2}
 \end{figure}
@@
 The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles.
-Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text:
-\begin{enumerate}
-\item True Positive is when the item is observed and predicted.
-\item True Negative is when the item is observed but not predicted.
-\item False Positive is when the item is not observed but still predicted.
-\item False Negative is when the item is neither observed nor predicted..
-\end{enumerate}
-
+Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text.
 The following confusion matrices allow us to analyze the results for each roaming agreement:

### 2021-08-27 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.3

@@
 Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}.
-However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
+However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
+In this regard, it is possible to establish 3 stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
 
@@
 \begin{enumerate}
-\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of entities, amounts and others.
+\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.
 
@@
 Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitalization system for RA drafting negotiations.
-For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a digitization process of negotiation procedures for a transparent drafting of Roaming Agreements.
+For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine.
+This NLP engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
 The NLP engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
@@
 Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}.
-Therefore, the similarity falls within the comparison approach.
-In this regard, our work distinguishes between two types of similarities: Jaccard similarity and Cosine similarity \cite{Gupta2018}.
-While the first one is established as the size of the intersection divided by the size of the union of two sets, the second one implies the determination of the cosine of the angle between two vectors.
+Therefore, the \textit{similarity} falls within the comparison approach.
+In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
 
@@
 Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports.
+Regarding the implementation of the \textit{similarity} it should be noted that it has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.
 
@@
 
+\begin{table}[htbp]
+\caption{Confusion Matrix for Proximus Roaming Agreement}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{n = 100} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
+\hline
+\textbf{\textit{stdClause}}& 57 & 2 & 5 \\
+\hline
+\textbf{\textit{variation}}& 8 & 31 & 0 \\
+\hline
+\textbf{\textit{customText}}& 7 & 9 & 25 \\
+\hline
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\begin{table}[]
+\caption{Confusion Matrix for Orange Roaming Agreement}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{n = 100} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
+\hline
+\textbf{\textit{stdClause}}& 57 & 2 & 5 \\
+\hline
+\textbf{\textit{variation}}& 8 & 31 & 0 \\
+\hline
+\textbf{\textit{customText}}& 7 & 9 & 25 \\
+\hline
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
 \subsection{Accuracy determination based on symbol comparison}
@@
 
-The following radar plots allow us to analyze the results for each roaming agreement:
+The following clustered column chart allow us to analyze the results for each roaming agreement:
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
+\caption{NLP Engine overall architecture.}
+\label{fig3}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
+\caption{NLP Engine overall architecture.}
+\label{fig4}
+\end{figure}
 

### 2021-08-27 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.4

@@
 Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text.
-The following confusion matrices allow us to analyze the results for each roaming agreement:
+The following confusion matrices allow us to analyze the results for each sample roaming agreements.
+In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily identified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
+Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.
+Therefore, it is possible to affirm that the predictive capacity of the NLP Engine for the Proximus sample roaming agreement is satisfactory.
 
 \begin{table}[htbp]
-\caption{Confusion Matrix for Proximus Roaming Agreement}
+\caption{Confusion Matrix for Proximus Roaming Agreement.}
 \begin{center}
@@
 \hline
-\textbf{n = 100} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
+\textbf{n = 72} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
 \hline
-\textbf{\textit{stdClause}}& 57 & 2 & 5 \\
+\textbf{\textit{stdClause}}& 21 & 3 & 1 \\
 \hline
-\textbf{\textit{variation}}& 8 & 31 & 0 \\
+\textbf{\textit{variation}}& 2 & 35 & 4 \\
 \hline
-\textbf{\textit{customText}}& 7 & 9 & 25 \\
+\textbf{\textit{customText}}& 0 & 1 & 5 \\
 \hline
 \end{tabular}
-\label{tab1}
+\label{table1}
 \end{center}
@@
 
-\begin{table}[]
-\caption{Confusion Matrix for Orange Roaming Agreement}
+The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine identifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement.
+Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
+
+\begin{table}[htbp]
+\caption{Confusion Matrix for Orange Roaming Agreement.}
 \begin{center}
@@
 \hline
-\textbf{n = 100} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
+\textbf{n = 86} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
 \hline
-\textbf{\textit{stdClause}}& 57 & 2 & 5 \\
+\textbf{\textit{stdClause}}& 14 & 0 & 1 \\
 \hline
-\textbf{\textit{variation}}& 8 & 31 & 0 \\
+\textbf{\textit{variation}}& 1 & 8 & 0 \\
 \hline
-\textbf{\textit{customText}}& 7 & 9 & 25 \\
+\textbf{\textit{customText}}& 4 & 1 & 57 \\
 \hline
 \end{tabular}
-\label{tab1}
+\label{table2}
 \end{center}
@@
 The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
-For that purpose, the text comparison tool Countwordsfree(\cite{countwordsfree}) is used manually copying sub-article by sub-article.
+This comparison is performed at the symbol level, considering the order of appearance of each symbol.
+For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used manually copying sub-article by sub-article.
 For each sub-article is determined:
@@
 \begin{enumerate}
-\item Common percentage of words between compared sub-articles.
-\item Difference percentage of words between compared sub-articles.
-\item Common words between compared sub-articles.
-\item Difference words between compared sub-articles.
+\item Common percentage of symbols between compared sub-articles.
+\item Difference percentage of symbols between compared sub-articles.
+\item Common symbols between compared sub-articles.
+\item Difference symbols between compared sub-articles.
 \end{enumerate}
 
-The following clustered column chart allow us to analyze the results for each roaming agreement:
+The following radar chart allow us to analyze the results for each roaming agreement.
+Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement.
+The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
+Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement.
+In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of unwanted characters at the time of popularization in the output file, thus improving the results obtained for the Proximus sample roaming agreement.
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
-\caption{NLP Engine overall architecture.}
+\centerline{\includegraphics[width=0.43\textwidth]{images/Proximus.png}}
+\caption{Common percentage of symbols for Proximus Roaming Agreement.}
 \label{fig3}
@@
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
-\caption{NLP Engine overall architecture.}
+\centerline{\includegraphics[width=0.43\textwidth]{images/Orange.png}}
+\caption{NLP Engine overall architecture for Orange Roaming Agreement.}
 \label{fig4}

### 2021-08-28 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
27.08.21.5

@@
 The flow chart in Fig.~\ref{fig1} is a general scheme of the methodology designed for the NLP Engine, which will be explained in detail below.
+
+The starting point of the methodology is the detection of PDF files.
+The file name is used as one of the identifiers of the output file.
+The next step is to find similarities in document texts so that headers and footers can be detected.
+The resources to use to detect are font size and font weight.
+Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed.
+Once the parsing phase has been completed, on the one hand, \textit{detection} and on the other hand, \textit{comparison} is performed.
+
+The detection phase presents a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
+For this reason, the text is segmented into 100 symbols by 100 symbols.
 

### 2021-08-28 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.1

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract. This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+Roaming is the capability of a subscriber to have persistence of service in a mobile network managed by a different operator.
+To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement.
+Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase.
+To address the lack of transparency contained in this stage, this paper proposes the use of a Natural Language Processing engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+In addition to the NLP Engine design, the implementation and testing are carried out as part of an experimentation phase to measure the accuracy at which the output file has been populated.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-NLP, Roaming Agreement, Amazon Comprehend, Similarity
+Natural Language Processing, NLP, Roaming Agreement, Amazon Comprehend, Similarity
 \end{IEEEkeywords}
@@
 In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
-Reference \cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
+Reference~\cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
@@
 The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles.
-Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each item, i.e., variable, variation, standard clause and custom text.
+Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each sub-article, i.e., variable, variation, standard clause and custom text.
 The following confusion matrices allow us to analyze the results for each sample roaming agreements.
@@
 \section{Conclusions}
-Considering that the proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems, as well as the integration of the NLP Engine part.
+The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as standard clauses, variations and customized texts.
+The test phase allows to evaluate the results obtained from two types of experiments carried out to measure the accuracy.
+The results show on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the detection of standard clauses, an accuracy of 82.9\% in the detection of variations and an accuracy of 80\% in the detection of personalized texts.
+These results improve for the second sample roaming agreement with an accuracy of 92.9\% in the detection of standard clauses, an accuracy of 87.5\% in the detection of variations and an accuracy of 91.2\% in the detection of custom texts.
+On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols.
+This result also improves for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols.
+Therefore, the results demonstrate the feasibility of applying the proposed methodology.
+Although the results demonstrate the feasibility of the designed methodology, as part of a process of continuous improvement within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity.
+
+The proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems, as well as the integration of the NLP Engine part.
 

### 2021-08-28 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.2

@@
 In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
-Reference~\cite{ROCCO2017} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
+Rocco \footnote{Rocco Group: https://www.rocco.group} provides a list of the most commonly used GSMA standards, which are summarized bellow \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
@@
 
-However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e.
-the MNOs, still use asynchronous flows such as email or even regular mail for information exchange.
-Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitalization system for RA drafting negotiations.
+However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e.
+the MNOs, still use asynchronous flows such as e-mail or even regular mail for the exchange of information.
+On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs.
+On the other hand, this process is a waste of time.
+As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
+It is necessary to provide a transparent digitization system for RA drafting negotiations, allowing only a few days or even hours to be spent.
 For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine.
@@
 
-The rest of this manuscript is structured as follows: Section 2 reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems as part of related work.
+The rest of this manuscript is structured as follows: Section 2 analyzes the related work in order to determine the novelty of the proposed topic.
 Section 3 establishes the designed methodology.
@@
 \section{Related work}
+
+This section reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems.
 
@@
 Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}.
-While \textit{detection} has words as its basic processing unit, \textit{comparison} has sub-articles as its basic processing unit.
+While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit.
 \textit{Detection} represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement.
-\textit{Comparison} represents the capacity to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
-For example, while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
+In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
+
+\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
+In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}.
+In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
+As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
 Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial name of a MNO and the start date of the agreement.
-The technologies that enable both \textit{detection} and \textit{comparison} are discussed below as part of the \textit{background}.
-The third section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.
-
-\subsection{Amazon comprehend}
-In short, \textit{Amazon Comprehend} is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
-The capabilities that \textit{Amazon Comprehend} integrates are key in the \textit{detection} approach.
-
-\subsection{Similarity Analysis}
-Similarity is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}.
-Therefore, the \textit{similarity} falls within the comparison approach.
-In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
+The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.
 
@@
 
-The detection phase presents a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
-For this reason, the text is segmented into 100 symbols by 100 symbols.
+The \textit{detection} phase presents a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
+For this reason, the text is segmented into pieces of 100 symbols.
+For each symbol packet the API outputs entities, key phrases and sentiment in a JSON format (\cite{AWS2021}), which must be grouped and further processed.
+The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'.
+In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the element stored in the 'Text' field.
+Once this filtering is done, the processing is carried out based on sorting forms, for which the designed logic is particularized according to the type of varaibles to be detected.
+For example, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases.
+The detected variables are stored to be used later to determine which ones are part of the variations.
 
@@
 \end{figure}
+
+The \textit{comparison} phase implies a complex pre-processing in order to separate by articles and then in sub-articles.
+Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template.
+After that, \textit{Jaccard's similarity} associates a score to the sub-article id.
+A score greater than 0.85 (score $\geq$ 0.85) is considered a standard clause, a value less than 0.15 (score $\leq$ 0.15) is considered a custom text and a value between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85) is considered a variation.
+At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation}, the \textit{variables} that it contains.
 
@@
 The following confusion matrices allow us to analyze the results for each sample roaming agreements.
-In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily identified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
+In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
 Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.
-Therefore, it is possible to affirm that the predictive capacity of the NLP Engine for the Proximus sample roaming agreement is satisfactory.
 
@@
 
-The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine identifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement.
-Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
-
 \begin{table}[htbp]
@@
 \label{table2}
+\end{center}
+\end{table}
+
+The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement.
+Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
+
+Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
+Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted is the greater detection capacity of the NLP Engine in one document with respect to another.
+
+\begin{table}[htbp]
+\caption{Summary of accuracy determination for simple inspection at sub-article level.}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{} & \textbf{\textit{Proximus}}& \textbf{\textit{Orange}} \\
+\hline
+\textbf{\textit{stdClause}}& 80.9\% & 92.9\% \\
+\hline
+\textbf{\textit{variation}}& 82.9\% & 87.5\% \\
+\hline
+\textbf{\textit{customText}}& 80.0\% & 91.2\% \\
+\hline
+\end{tabular}
+\label{table3}
 \end{center}

### 2021-08-28 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.4

@@
 The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
+
 Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement.
-In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of unwanted characters at the time of popularization in the output file, thus improving the results obtained for the Proximus sample roaming agreement.
+In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
 

### 2021-08-29 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
28.08.21.6

@@
 \begin{abstract}
-Roaming is the capability of a subscriber to have persistence of service in a mobile network managed by a different operator.
+Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator.
 To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement.
-Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase.
-To address the lack of transparency contained in this stage, this paper proposes the use of a Natural Language Processing engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-In addition to the NLP Engine design, the implementation and testing are carried out as part of an experimentation phase to measure the accuracy at which the output file has been populated.
+Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase, which on the one hand do not ensure transparency and on the other hand constitute a waste of time with duration of up to one month.
+To address the lack of transparency and reduce wasted time, this paper proposes the use of a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+The Natural Language Processing Engine not only is designed but also is implemented and tested.
+Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Natural Language Processing, NLP, Roaming Agreement, Amazon Comprehend, Similarity
+Natural Language Processing, Telecommunication, Roaming Agreement, Amazon Comprehend, Similarity
 \end{IEEEkeywords}
@@
 
-\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties, currencies and so on with respect to the original text, i.e., the GSMA standard templates.
+\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.
 
@@
 However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e.
-the MNOs, still use asynchronous flows such as e-mail or even regular mail for the exchange of information.
+the MNOs, still use asynchronous flows such as e-mail or even regular mail for the information exchange.
 On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs.
@@
 As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
-It is necessary to provide a transparent digitization system for RA drafting negotiations, allowing only a few days or even hours to be spent.
+Therefore, it is necessary to provide a transparent digitization system for RA drafting negotiations, which guarantees the use of a few days or even hours.
 For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine.
-This NLP engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The NLP engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
-For this purpose, the NLP engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
+This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+The NLP Engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
+For this purpose, the NLP Engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
 The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool.
-This article includes not only the design phase, but also the implementation and evaluation of the tool.
+This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.
 
@@
 A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.
-This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitalization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
+This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
 The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
@@
 
-Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary.
+Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as judiciary.
 Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
@@
 While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit.
-\textit{Detection} represents the capability to locate \textit{variables} in a text file, i.e., the Roaming Agreement.
+\textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the Roaming Agreement.
 In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
@@
 \textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
-In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is used to compare different types of data, so it is a resource used for pattern classification, clustering and information retrieval problems \cite{7429408}.
+In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering and information retrieval problems \cite{7429408}.
 In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
 As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
-Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial name of a MNO and the start date of the agreement.
+Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA.
 The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.
@@
 The file name is used as one of the identifiers of the output file.
-The next step is to find similarities in document texts so that headers and footers can be detected.
-The resources to use to detect are font size and font weight.
+The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters.
+For that purpose, the mechanism used is the detection of different font size and weight.
 Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed.
-Once the parsing phase has been completed, on the one hand, \textit{detection} and on the other hand, \textit{comparison} is performed.
+It is now possible to perform both \textit{detection} and \textit{comparison}.
 
-The \textit{detection} phase presents a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
+The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
 For this reason, the text is segmented into pieces of 100 symbols.
@@
 The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'.
-In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the element stored in the 'Text' field.
-Once this filtering is done, the processing is carried out based on sorting forms, for which the designed logic is particularized according to the type of varaibles to be detected.
-For example, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases.
-The detected variables are stored to be used later to determine which ones are part of the variations.
+In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field.
+Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree.
+The designed logic is particularized according to the type of \textit{variable} to be detected.
+For instance, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases.
+The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.
 
@@
 
-The \textit{comparison} phase implies a complex pre-processing in order to separate by articles and then in sub-articles.
-Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template.
-After that, \textit{Jaccard's similarity} associates a score to the sub-article id.
-A score greater than 0.85 (score $\geq$ 0.85) is considered a standard clause, a value less than 0.15 (score $\leq$ 0.15) is considered a custom text and a value between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85) is considered a variation.
-At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation}, the \textit{variables} that it contains.
+The \textit{comparison} phase implies to separate by articles and then by sub-articles.
+Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template and therefore, to establish comparisons at sub-article level.
+\textit{Jaccard's similarity} associates a score to the sub-article id.
+Thus, an sub-article is considered a \textit{standard clause} whether the score assigned is greater than 0.85 (score $\geq$ 0.85).
+In addition, a sub-article is considered a \textit{custom text} whether the score assigned is less than 0.15 (score $\leq$ 0.15).
+Finally, a sub-article is considered a \textit{variation} whether the score assigned is between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85).
+At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation} or \textit{customized texts}, the \textit{variables} that it contains.
 
@@
 The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts.
-First, the input files include the Roaming Agreement text file as well as the GSMA standard templates.
+Thus, the input files include the Roaming Agreement text file as well as the GSMA standard templates.
 The processing layer includes the logic associated with the NLP engine, i.e.
@@
 The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
-Each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as a variation.
+In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.
 
@@
 
-Regarding the input and output files, these are associated to the container through volumes.
+The input and output files are associated to the container through volumes.
 In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point.
@@
 Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS).
-The NLP Engine imports the service associated to Amazon Comprehend.
-Other library imported into NLP Engine library is PyMuPDF (\cite{PyMuPDF}), which is used by the NLP Engine to extract headers and footers from the PDF files.
+The NLP Engine imports the specific service associated to Amazon Comprehend.
+PyMuPDF (\cite{PyMuPDF}) constitutes other library imported into the NLP Engine to be used into headers and footers detection.
 Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports.
-Regarding the implementation of the \textit{similarity} it should be noted that it has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.
+The \textit{similarity} has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.
 
@@
 On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison.
-The tests will be performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}.
+The tests are performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}.
 Each experiment is described below and the results obtained are discussed in the same section.
@@
 \subsection{Accuracy determination based on a simple inspection at sub-article level}
-The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a variation, a standard clause or a customized text with respect to the GSMA standard template.
-Additionally, the detected variables are analyzed.
-The results obtained are then compared with the values populated in the NLP Engine output file, for the same articles.
-Considering that the results obtained from the simple inspection constitute the observations and the values collected from the article and sub-article classification file constitute the predicted values, it is considered for each sub-article, i.e., variable, variation, standard clause and custom text.
-The following confusion matrices allow us to analyze the results for each sample roaming agreements.
+The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} with respect to the GSMA standard template.
+The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article.
+Considering that the results obtained from the simple inspection constitute the observations and the values collected from sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample roaming agreements.
 In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
 Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.
+Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
 
@@
 Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
-
-Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
-Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted is the greater detection capacity of the NLP Engine in one document with respect to another.
+Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
 
@@
 
+Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document with respect to another.
+
 \subsection{Accuracy determination based on symbol comparison}
@@
 The following radar chart allow us to analyze the results for each roaming agreement.
+The radar chart contain in the inner radius the Common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article.
 Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement.
-The conclusion that can be reached by simple inspection is that only 11 of the 72 analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
+The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
 
-Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of words between the sub-articles compared for the Orange sample roaming agreement.
-In this case, only 7 of the 86 analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
+Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement.
+In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
 
@@
 \section{Conclusions}
-The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as standard clauses, variations and customized texts.
-The test phase allows to evaluate the results obtained from two types of experiments carried out to measure the accuracy.
-The results show on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the detection of standard clauses, an accuracy of 82.9\% in the detection of variations and an accuracy of 80\% in the detection of personalized texts.
-These results improve for the second sample roaming agreement with an accuracy of 92.9\% in the detection of standard clauses, an accuracy of 87.5\% in the detection of variations and an accuracy of 91.2\% in the detection of custom texts.
+The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
+The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and an accuracy of 80\% in the classification of \textit{customized texts}.
+These results are improved for the second sample roaming agreement with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}.
 On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols.
-This result also improves for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols.
+This result is also improved for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols.
 Therefore, the results demonstrate the feasibility of applying the proposed methodology.
-Although the results demonstrate the feasibility of the designed methodology, as part of a process of continuous improvement within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity.
+As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity in order to improve the results obtained.
 

### 2021-08-30 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
30.08.21.1

@@
 Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator.
-To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement.
-Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase, which on the one hand do not ensure transparency and on the other hand constitute a waste of time with duration of up to one month.
-To address the lack of transparency and reduce wasted time, this paper proposes the use of a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The Natural Language Processing Engine not only is designed but also is implemented and tested.
+To achieve this persistence of connectivity it is necessary for operators to agree on technical, commercial and legal aspects in what is known as a Roaming Agreement.
+Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail.
+The most important and affecting period within the roaming agreement is known as the drafting phase as it did not ensure transparency and it  is time consuming.
+To address the lack of transparency and reduce wasted time, this paper proposes a framework that automate the process of drafting the roaming agreement and enable better accessibility.
+The proposed framework exploits a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+Extensive experiments on real roaming agreements show the superiority of our proposed framework in drafting the roaming agreements against the traditional drafting negotiation process with prediction accuracy over 80.0\%.
+% The Natural Language Processing Engine not only is designed but also is implemented and tested.
 Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
@@
 \begin{IEEEkeywords}
-Natural Language Processing, Telecommunication, Roaming Agreement, Amazon Comprehend, Similarity
+Roaming Agreement, Natural Language Processing, Telecommunication
 \end{IEEEkeywords}
@@
 However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
-In this regard, it is possible to establish 3 stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
+In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
+The testing and implementation phases are straight forward as they are related with implementing what is agreed on the drafting phase.
+However, the drafting phase is ambiguous and needs a lot of efforts from both parties, i.e.
+the MNOs.
 
-In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
-Rocco \footnote{Rocco Group: https://www.rocco.group} provides a list of the most commonly used GSMA standards, which are summarized bellow \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
+Therefore, in order to reduce the exerted efforts and standardize technical, commercial and legal aspects of the RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
+In addition, many organizations attempt to unify RAs.
+For example, Rocco\footnote{Rocco Group: https://www.rocco.group}, which is a company specialized in telecommunication reports including roaming agreements, provides a list of the most commonly used GSMA standards.
+It summarizes these standards as follows \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
-While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}.
-Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
-Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates to determine whether:
+While it is true that it is not mandatory to follow the standards proposed by the GSMA organization, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}.
+Therefore, the first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
+Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates.
+This necessitates discretizing the bulk of the roaming agreement template and classifying each word/clause from an existing classes as follows:
 
@@
 \item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.
-
-\item Leave an article/sub-article as found in the template thereby establishing a \textit{standard clause}.
-
 \item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.
-
+\item Leave an article/sub-article as found in the template (RA draft); thereby establishing a \textit{standard clause}.
 \item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.
-
 \end{enumerate}
 
-However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e.
-the MNOs, still use asynchronous flows such as e-mail or even regular mail for the information exchange.
-On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs.
-On the other hand, this process is a waste of time.
-As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
-Therefore, it is necessary to provide a transparent digitization system for RA drafting negotiations, which guarantees the use of a few days or even hours.
-For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine.
+However, the \textit{drafting} of a RA goes through a complex negotiation process in which, at present, the parties still use asynchronous flows such as e-mail or even regular mail to exchange the information.
+Thus, this traditional negotiation process has multiple drawbacks including lacks of transparency, which can lead to violations of the RA by MNOs.
+In addition, this process is laborious and time consuming.
+As Rocco points out, the entire process can take up to one month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
+Therefore, it is necessary to provide a transparent digitalization system for RA drafting negotiations, which guarantees transparency and shortening the negotiation time, which could be a couple of days or even hours.
+Hence, this work develops a framework that exploits the advancement in the Natural Language Processing (NLP) discipline and use it as a legal text digitalization engine.
 This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The NLP Engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
-For this purpose, the NLP Engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
+The proposed NLP Engine analyzes articles and sub-articles of the RA by determining the existence of variables, variations, standard clauses and customized texts.
+To do so, the proposed NLP Engine relies on the advancement of NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) in drafting RAs.
+
+% using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
 The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool.
@@
 
-The rest of this manuscript is structured as follows: Section 2 analyzes the related work in order to determine the novelty of the proposed topic.
+% The rest of this manuscript is structured as follows: Section 2 presents the related work in order to determine the novelty of the proposed topic.
 Section 3 establishes the designed methodology.
@@
 
-This section reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems.
+The existing work that is related to the roaming agreements can be categorized into two main categories.
+The first category encompasses the work, which focused on transparent digitalization of roaming agreements~\cite{9369516, 9024541, Huillet2020}, whereas the second category includes the work that apply existing NLP techniques-based text processing systems~\cite{8487847, 9138070, 9104105}.
 
@@
 The interaction between the two entities takes place through an Ethereum based platform.
+Despite the contributions of this work in the roaming agreement implementation phase, the fact of performing the implementation on the Ethereum network implies that the transactions cost must be born among the participating MNOs.
+Additionally, although the authors justify the latency given that they repeated the experiment 100 times, the non-deterministic nature of the network implies that may suffer congestion anytime.
 A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.

### 2021-08-30 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
30.08.21.2

@@
 A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.
-This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
+This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.Although this work also constitutes an important contribution regarding the use of Hyperledger Fabric Blockchain in the field of telecommunications to address problems around Managing Roaming Agreements, Inter-carrier Settlements, and Mobile Number Portability, its approach is one of review and proposal, however, it lacks an implementation stage that would allow demonstrating the feasibility of the proposals.
 The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
-Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.
+This proposal is also of considerable value in the business environment, however, its focus relates only to the implementation phase of the roaming agreement and not to the drafting phase.
 
@@
 Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
-This linguistic analysis attempts to find the appropriate meaning of terms within a document.
+The proposed article also constitutes an important contribution in terms of the design of the linguistic analysis based on NLP techniques, however, it lacks formal evaluation in terms of accuracy in terms of NLP implementation.
 In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
-NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.
+NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied.
 Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend.
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
+Although the value of the contribution lies in the use of NLP techniques from the Amazon Comprehend tool, the paper lacks a formal results section, therefore it is difficult to determine the accuracy of the tool.
 Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement.
@@
 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
+\caption{Overview of the designed methodology.}
+\label{fig1}
+\end{figure}
+
 The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
@@
 The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
-\caption{Overview of the designed methodology.}
-\label{fig1}
-\end{figure}
 
@@
 
-Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement.
-In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
-
 \begin{figure}[htbp]
@@
 \end{figure}
+
+Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement.
+In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
 

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
30.08.21.3
31.08.21.1

--- 2021-08-29 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-\usepackage[sorting=none]{biblatex}
+\usepackage[style=ieee, backend=biber, sorting=none]{biblatex}
 \addbibresource{references/references.bib}
@@
 Roaming is the capability of a subscriber to have persistence of service in a visited mobile network managed by a different operator.
-To achieve this persistence of connectivity it is necessary for operators to agree on technical, legal and commercial aspects in what is known as a Roaming Agreement.
-Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail within the agreement drafting phase, which on the one hand do not ensure transparency and on the other hand constitute a waste of time with duration of up to one month.
-To address the lack of transparency and reduce wasted time, this paper proposes the use of a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The Natural Language Processing Engine not only is designed but also is implemented and tested.
+To achieve this persistence of connectivity, it is necessary for operators to agree on technical, commercial and legal aspects in what is known as a Roaming Agreement.
+Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail.
+The main phase in building the roaming agreement is known as the drafting phase, which is a time consuming process with limited assurance and transparency on handling the drafting events.
+To address the lack of transparency and reduce the drafting time, this paper proposes a framework that automate the process of drafting and negotiation of the roaming agreement and enable better accessibility.
+The proposed framework exploits a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+Extensive experiments on real roaming agreements show the superiority of our proposed framework in drafting the roaming agreements against the traditional drafting and negotiation process with prediction accuracy over 80.0\%.
+% The Natural Language Processing Engine not only is designed but also is implemented and tested.
 Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
@@
 \begin{IEEEkeywords}
-Natural Language Processing, Telecommunication, Roaming Agreement, Amazon Comprehend, Similarity
+Roaming Agreement, Natural Language Processing, Telecommunication
 \end{IEEEkeywords}
 
-\section{Introduction}
-The roaming service maintains the persistent connectivity of subscribers in different networks and locations.
-Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}.
-However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
-In this regard, it is possible to establish 3 stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
-
-In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
-Rocco \footnote{Rocco Group: https://www.rocco.group} provides a list of the most commonly used GSMA standards, which are summarized bellow \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
-
-While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}.
-Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
-Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates to determine whether:
-
-\begin{enumerate}
-\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.
-
-\item Leave an article/sub-article as found in the template thereby establishing a \textit{standard clause}.
-
-\item Introduce certain \textit{variations} in the articles/sub-articles, by changing \textit{variables}, e.g., MNO commercial name, dates, penalties.
-
-\item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.
-
-\end{enumerate}
-
-However, the drafting of a RA goes through a complex negotiation process in which, at present, the parties, i.e.
-the MNOs, still use asynchronous flows such as e-mail or even regular mail for the information exchange.
-On the one hand, this process lacks transparency, which can lead to violation of the RA by MNOs.
-On the other hand, this process is a waste of time.
-As Rocco points out, the entire process can be to up 1 month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
-Therefore, it is necessary to provide a transparent digitization system for RA drafting negotiations, which guarantees the use of a few days or even hours.
-For this reason, this paper proposes the use of Natural Language Processing (NLP) as a legal text digitization engine.
-This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The NLP Engine analyzes articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts.
-For this purpose, the NLP Engine relies on the one hand, on NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques.
-The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool.
-This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.
-
-The rest of this manuscript is structured as follows: Section 2 analyzes the related work in order to determine the novelty of the proposed topic.
-Section 3 establishes the designed methodology.
-The implementation of our system are described in Section 4.
-Section 5 discusses the results of conducted experiments.
-Finally, the conclusions of the manuscript are included in Section 6.
-
-\section{Related work}
-
-This section reviews both the attempts at transparent digitalization of roaming agreements and existing NLP techniques-based text processing systems.
-
-Both in the scientific literature and in business environments there are important approaches to RA digitalization.
-Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO.
-The interaction between the two entities takes place through an Ethereum based platform.
-A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}.
-This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.
-The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}.
-Despite the value of these contributions from a RA implementation perspective, they are not within the context of a transparent digitalization to improve the negotiation process for the effective drafting of the roaming agreement.
-
-Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as judiciary.
-Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques.
-This linguistic analysis attempts to find the appropriate meaning of terms within a document.
-In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information.
-NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.
-Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend.
-This system performs an audio-to-text transcription and then performs the processing of the obtained text.
-Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement.
-Therefore, we can affirm that our work introduces a topic with a high degree of novelty.
-
-\section{NLP Engine methodology}
-Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}.
-While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit.
-\textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the Roaming Agreement.
-In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
-
-\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template.
-In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering and information retrieval problems \cite{7429408}.
-In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
-As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}.
-Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA.
-The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.
-
-\subsection{Designed Methodology}
-The flow chart in Fig.~\ref{fig1} is a general scheme of the methodology designed for the NLP Engine, which will be explained in detail below.
-
-The starting point of the methodology is the detection of PDF files.
-The file name is used as one of the identifiers of the output file.
-The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters.
-For that purpose, the mechanism used is the detection of different font size and weight.
-Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed.
-It is now possible to perform both \textit{detection} and \textit{comparison}.
-
-The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API.
-For this reason, the text is segmented into pieces of 100 symbols.
-For each symbol packet the API outputs entities, key phrases and sentiment in a JSON format (\cite{AWS2021}), which must be grouped and further processed.
-The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'.
-In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field.
-Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree.
-The designed logic is particularized according to the type of \textit{variable} to be detected.
-For instance, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases.
-The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
-\caption{Overview of the designed methodology.}
-\label{fig1}
-\end{figure}
-
-The \textit{comparison} phase implies to separate by articles and then by sub-articles.
-Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template and therefore, to establish comparisons at sub-article level.
-\textit{Jaccard's similarity} associates a score to the sub-article id.
-Thus, an sub-article is considered a \textit{standard clause} whether the score assigned is greater than 0.85 (score $\geq$ 0.85).
-In addition, a sub-article is considered a \textit{custom text} whether the score assigned is less than 0.15 (score $\leq$ 0.15).
-Finally, a sub-article is considered a \textit{variation} whether the score assigned is between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85).
-At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation} or \textit{customized texts}, the \textit{variables} that it contains.
-
-\section{Implemented System}
-The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts.
-Thus, the input files include the Roaming Agreement text file as well as the GSMA standard templates.
-The processing layer includes the logic associated with the NLP engine, i.e.
-the implementation of the designed methodology.
-The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
-In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
-\caption{NLP Engine overall architecture.}
-\label{fig2}
-\end{figure}
-
-The input and output files are associated to the container through volumes.
-In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point.
-Although the NLP Engine constitutes a library, it must in turn integrate other libraries, among which boto3 \cite{boto3}.
-Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS).
-The NLP Engine imports the specific service associated to Amazon Comprehend.
-PyMuPDF (\cite{PyMuPDF}) constitutes other library imported into the NLP Engine to be used into headers and footers detection.
-Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports.
-The \textit{similarity} has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.
-
-\section{Discussion of Results}
-Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated.
-For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results.
-On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison.
-The tests are performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}.
-Each experiment is described below and the results obtained are discussed in the same section.
-
-\subsection{Accuracy determination based on a simple inspection at sub-article level}
-The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} with respect to the GSMA standard template.
-The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article.
-Considering that the results obtained from the simple inspection constitute the observations and the values collected from sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample roaming agreements.
-In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
-Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.
-Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
-
-\begin{table}[htbp]
-\caption{Confusion Matrix for Proximus Roaming Agreement.}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{n = 72} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
-\hline
-\textbf{\textit{stdClause}}& 21 & 3 & 1 \\
-\hline
-\textbf{\textit{variation}}& 2 & 35 & 4 \\
-\hline
-\textbf{\textit{customText}}& 0 & 1 & 5 \\
-\hline
-\end{tabular}
-\label{table1}
-\end{center}
-\end{table}
-
-\begin{table}[htbp]
-\caption{Confusion Matrix for Orange Roaming Agreement.}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{n = 86} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
-\hline
-\textbf{\textit{stdClause}}& 14 & 0 & 1 \\
-\hline
-\textbf{\textit{variation}}& 1 & 8 & 0 \\
-\hline
-\textbf{\textit{customText}}& 4 & 1 & 57 \\
-\hline
-\end{tabular}
-\label{table2}
-\end{center}
-\end{table}
-
-The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement.
-Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
-Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
-
-\begin{table}[htbp]
-\caption{Summary of accuracy determination for simple inspection at sub-article level.}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{} & \textbf{\textit{Proximus}}& \textbf{\textit{Orange}} \\
-\hline
-\textbf{\textit{stdClause}}& 80.9\% & 92.9\% \\
-\hline
-\textbf{\textit{variation}}& 82.9\% & 87.5\% \\
-\hline
-\textbf{\textit{customText}}& 80.0\% & 91.2\% \\
-\hline
-\end{tabular}
-\label{table3}
-\end{center}
-\end{table}
-
-Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document with respect to another.
-
-\subsection{Accuracy determination based on symbol comparison}
-The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
-This comparison is performed at the symbol level, considering the order of appearance of each symbol.
-For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used manually copying sub-article by sub-article.
-For each sub-article is determined:
-
-\begin{enumerate}
-\item Common percentage of symbols between compared sub-articles.
-\item Difference percentage of symbols between compared sub-articles.
-\item Common symbols between compared sub-articles.
-\item Difference symbols between compared sub-articles.
-\end{enumerate}
-
-The following radar chart allow us to analyze the results for each roaming agreement.
-The radar chart contain in the inner radius the Common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article.
-Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement.
-The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
-
-Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement.
-In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.43\textwidth]{images/Proximus.png}}
-\caption{Common percentage of symbols for Proximus Roaming Agreement.}
-\label{fig3}
-\end{figure}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.43\textwidth]{images/Orange.png}}
-\caption{NLP Engine overall architecture for Orange Roaming Agreement.}
-\label{fig4}
-\end{figure}
-
-\section{Conclusions}
-The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
-The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and an accuracy of 80\% in the classification of \textit{customized texts}.
-These results are improved for the second sample roaming agreement with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}.
-On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols.
-This result is also improved for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols.
-Therefore, the results demonstrate the feasibility of applying the proposed methodology.
-As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity in order to improve the results obtained.
-
-The proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems, as well as the integration of the NLP Engine part.
+\input{sections/Introduction}
+\input{sections/Related_Work}
+\input{sections/Methods}
+\input{sections/Results}
+\input{sections/Conclusion}
 
 \printbibliography
-
-\vspace{12pt}
-
 \end{document}

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Conclusion.tex
31.08.21.1

\section{Conclusions}
The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as \textit{standard clauses}, \textit{variations} and \textit{customized texts}. The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and an accuracy of 80\% in the classification of \textit{customized texts}. These results are improved for the second sample roaming agreement with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}. On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols. This result is also improved for the second roaming agreement sample with an accuracy of 91.9\% of the total of 86 sub-articles analyzed with a common percentage of favorable symbols. Therefore, the results demonstrate the feasibility of applying the proposed methodology. As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity in order to improve the results obtained.

The proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems that mainly include the smart contracts that automate the negotiation process, as well as the integration with the developed NLP Engine.

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
31.08.21.1

\section{Introduction}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}. However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA). In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}. The testing and implementation phases are straight forward as they are related with implementing what is agreed on the drafting phase. However, the drafting phase is ambiguous and involves multiple iterations of exchange of draft text and proposed articles between both parties, i.e. the MNOs.

Therefore, in order to reduce the exerted efforts and standardize the technical, commercial and legal aspects of the RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}. 
In addition, many organizations attempt to unify RAs. For example, Rocco\footnote{Rocco Group: https://www.rocco.group}, which is a company specialized in telecommunication reports including roaming agreements, provides a list of the most commonly used GSMA standards. It summarizes these standards as follows \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).

While it is true that it is not mandatory to follow the standards proposed by the GSMA organization, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}. Therefore, the first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates. This necessitates discretizing the bulk of the roaming agreement template and classifying each word/clause from an existing classes as follows:

\begin{enumerate}
\item Specify the value of certain \textit{variables} that are found in a certain text, such as dates, names of MNOs, locations and others.
\item Introduce certain \textit{variations} in the articles/sub-articles, usually identified as part of the text with different paraphrasing.
\item Leave an article/sub-article as found in the template (RA draft); thereby establishing a \textit{standard clause}.
\item Introduce completely new articles/sub-articles that respond to particular interests by constituting \textit{customized texts}.
\end{enumerate}

However, the \textit{drafting} of a RA goes through a complex negotiation process in which, at present, the parties still use asynchronous flows such as e-mail or even regular mail to exchange the information. Thus, this traditional negotiation process has multiple drawbacks including lacks of transparency, which can lead to violations of the RA by MNOs. In addition, this process is laborious and time consuming. As experts point out, the entire process can take up to one month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}. Therefore, it is necessary to provide a transparent digitalization system for RA drafting negotiations, which guarantees transparency and shortening the negotiation time, which guarantees transparency and shortening the negotiation time, which could be in days or even weeks. Hence, this work develops a framework that exploits the advancement in the Natural Language Processing (NLP) discipline and use it as a legal text in the digitalization engine. This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements. The proposed NLP Engine analyzes articles and sub-articles of the RA by determining the existence of variables, variations, standard clauses and customized texts. To do so, the proposed NLP Engine relies on the advancement of NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) in drafting RAs.

% using the unstructured data information discovery tool \textit{Amazon Comprehend} and, on the other hand, by establishing an comprehensive comparison between texts based on \textit{similarity} determination techniques. The procedures for integrating tools, NLP techniques, pre-processing and post-processing constitute a methodological framework designed for the use case and included within an unstructured text processing tool. This article includes not only the design phase, but also the implementation and evaluation of the NLP Engine tool.

% The rest of this manuscript is structured as follows: Section 2 presents the related work in order to determine the novelty of the proposed topic. Section 3 establishes the designed methodology. The implementation of our system are described in Section 4. Section 5 discusses the results of conducted experiments. Finally, the conclusions of the manuscript are included in Section 6.

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Methods.tex
31.08.21.1

\section{NLP Engine methodology}
Overall, the logic designed for the NLP engine follows two approaches: \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the Roaming Agreement. In this regard, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content document by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the Roaming Agreement with respect to the sub-articles present in the GSMA standard template. In this regard, \textit{similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering and information retrieval problems \cite{7429408}. In this regard, our work uses  \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}. As result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the Roaming Agreement) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA. The next section integrates tools, NLP techniques, pre-processing and post-processing as part of the designed methodology.

\subsection{Designed Methodology}
The flow chart in Fig.~\ref{fig1} is a general scheme of the methodology designed for the NLP Engine, which will be explained in detail below.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
\caption{Overview of the designed methodology.}
\label{fig1}
\end{figure}

The starting point of the methodology is the detection of PDF files. The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters. For that purpose, the mechanism used is the detection of different font size and weight. Once the PDF format has been converted to text, headers and footers as well as undesired characters are removed. It is now possible to perform both \textit{detection} and \textit{comparison}.

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol packet the API outputs entities, key phrases and sentiment in a JSON format (\cite{AWS2021}), which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech' and 'Tag'. In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency' and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

The \textit{comparison} phase implies to separate by articles and then by sub-articles. Since, several of possibilities of articles names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template and therefore, to establish comparisons at sub-article level. \textit{Jaccard's similarity} associates a score to the sub-article id. Thus, an sub-article is considered a \textit{standard clause} whether the score assigned is greater than 0.85 (score $\geq$ 0.85). In addition, a sub-article is considered a \textit{custom text} whether the score assigned is less than 0.15 (score $\leq$ 0.15). Finally, a sub-article is considered a \textit{variation} whether the score assigned is between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85). At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation} or \textit{customized texts}, the \textit{variables} that it contains.

\section{Implemented System}
The Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated in a docker infrastructure that includes 3 parts. Thus, the input files include the Roaming Agreement text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JavaScript Object Notation (JSON) file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.23\textwidth]{images/NLP_Engine.png}}
\caption{NLP Engine overall architecture.}
\label{fig2}
\end{figure}

The input and output files are associated to the container through volumes. In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point. Although the NLP Engine constitutes a library, it must in turn integrate other libraries, among which boto3 \cite{boto3}. Boto3 is an Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS). The NLP Engine imports the specific service associated to Amazon Comprehend. PyMuPDF (\cite{PyMuPDF}) constitutes other library imported into the NLP Engine to be used into headers and footers detection. Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library, but must also install the libraries it imports. The \textit{similarity} has been implemented in a pluggable way, therefore at code level it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Related_Work.tex
31.08.21.1

\section{Related work}

The existing work that is related to the roaming agreements can be categorized into two main categories. The first category encompasses the work, which focused on transparent digitalization of roaming agreements~\cite{9369516, 9024541, Huillet2020}, whereas the second category includes the work that apply existing NLP techniques-based text processing systems~\cite{8487847, 9138070, 9104105}.

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. Despite the contributions of this work in the roaming agreement implementation phase, the fact of performing the implementation on the Ethereum network implies that the participating MNOs will bear the high cost of gas fees for the transactions. Additionally, although the authors justify the latency given that they repeated the experiment 100 times, the proof of work nature of the network implies drafting actions will suffer congestion anytime. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{9024541}. This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention.Although this work also constitutes an important contribution regarding the use of Hyperledger Fabric Blockchain in the field of telecommunications to address problems around Managing Roaming Agreements, Inter-carrier Settlements, and Mobile Number Portability, its approach is one of review and proposal, however, it lacks an implementation stage that would allow demonstrating the feasibility of the proposals. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{Huillet2020}. This proposal is also of considerable value in the business environment, however, its focus relates only to the implementation phase of the roaming agreement and not to the drafting phase.

Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as judiciary. Thus, the reference \cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. The proposed article also constitutes an important contribution in terms of the design of the linguistic analysis based on NLP techniques, however, it lacks formal evaluation in terms of accuracy in terms of NLP implementation. In addition, the reference \cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work.The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied. Finally, authors of reference \cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although the value of the contribution lies in the use of NLP techniques from the Amazon Comprehend tool, the paper lacks a formal results section, therefore it is difficult to determine the accuracy of the tool.

Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the roaming agreement. Therefore, and to the best of our knowledge, we can affirm that our work introduces a topic with a high degree of novelty.

### 2021-08-31 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Results.tex
31.08.21.1

\section{Discussion of Results}
Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated. For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results. On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison. The tests are performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}. Each experiment is described below and the results obtained are discussed in the same section.

\subsection{Accuracy determination based on a simple inspection at sub-article level}
The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} with respect to the GSMA standard template. The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article. Considering that the results obtained from the simple inspection constitute the observations and the values collected from sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample roaming agreements. In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable. Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives. Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

\begin{table}[htbp]
\caption{Confusion Matrix for Proximus Roaming Agreement.}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{n = 72} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
\hline
\textbf{\textit{stdClause}}& 21 & 3 & 1 \\
\hline
\textbf{\textit{variation}}& 2 & 35 & 4 \\
\hline
\textbf{\textit{customText}}& 0 & 1 & 5 \\
\hline
\end{tabular}
\label{table1}
\end{center}
\end{table}

\begin{table}[htbp]
\caption{Confusion Matrix for Orange Roaming Agreement.}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{n = 86} & \textbf{\textit{stdClause}}& \textbf{\textit{variation}}& \textbf{\textit{customText}} \\
\hline
\textbf{\textit{stdClause}}& 14 & 0 & 1 \\
\hline
\textbf{\textit{variation}}& 1 & 8 & 0 \\
\hline
\textbf{\textit{customText}}& 4 & 1 & 57 \\
\hline
\end{tabular}
\label{table2}
\end{center}
\end{table}

The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement. Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive. Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.

\begin{table}[htbp]
\caption{Summary of accuracy determination for simple inspection at sub-article level.}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{} & \textbf{\textit{Proximus}}& \textbf{\textit{Orange}} \\
\hline
\textbf{\textit{stdClause}}& 80.9\% & 92.9\% \\
\hline
\textbf{\textit{variation}}& 82.9\% & 87.5\% \\
\hline
\textbf{\textit{customText}}& 80.0\% & 91.2\% \\
\hline
\end{tabular}
\label{table3}
\end{center}
\end{table}

Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document with respect to another.

\subsection{Accuracy determination based on symbol comparison}
The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements. This comparison is performed at the symbol level, considering the order of appearance of each symbol. For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used manually copying sub-article by sub-article. For each sub-article is determined:

\begin{enumerate}
\item Common percentage of symbols between compared sub-articles.
\item Difference percentage of symbols between compared sub-articles.
\item Common symbols between compared sub-articles.
\item Difference symbols between compared sub-articles.
\end{enumerate}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.43\textwidth]{images/Proximus.png}}
\caption{Common percentage of symbols for Proximus Roaming Agreement.}
\label{fig3}
\end{figure}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.43\textwidth]{images/Orange.png}}
\caption{NLP Engine overall architecture for Orange Roaming Agreement.}
\label{fig4}
\end{figure}

The following radar chart allow us to analyze the results for each roaming agreement. The radar chart contain in the inner radius the Common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article. Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement. The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.

Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement. In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/paper.tex
01.08.21.1

@@
 \usepackage{cite}
+\usepackage{multirow}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \begin{document}
-\title{A methodological framework to enable the roaming agreement digitalization: An NLP-based approach\\}
+
+\title{A Natural Language Processing Approach for the Digitalization of Roaming Agreements\\}
 
@@
 Currently, Roaming Agreement negotiation uses asynchronous flow such as email or even regular mail.
-The main phase in building the roaming agreement is known as the drafting phase, which is a time consuming process with limited assurance and transparency on handling the drafting events.
-To address the lack of transparency and reduce the drafting time, this paper proposes a framework that automate the process of drafting and negotiation of the roaming agreement and enable better accessibility.
-The proposed framework exploits a Natural Language Processing Engine as a starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
+The main phase in building the roaming agreement is known as the drafting phase, which is a time-consuming process with limited assurance and transparency on handling the drafting events.
+To address the lack of transparency and reduce the drafting time, this paper proposes a framework that automates the process of drafting and negotiation of the roaming agreement and enables better accessibility.
+The proposed framework exploits a Natural Language Processing (NLP) engine as a starting point for the digitalization of the negotiation process towards transparent drafting of Roaming Agreements.
 Extensive experiments on real roaming agreements show the superiority of our proposed framework in drafting the roaming agreements against the traditional drafting and negotiation process with prediction accuracy over 80.0\%.
-% The Natural Language Processing Engine not only is designed but also is implemented and tested.
-Testing is performed as part of an experimentation phase to measure the accuracy at which the output file is populated regarding the original Roaming Agreement.
 \end{abstract}
@@
 \input{sections/Introduction}
-\input{sections/Related_Work}
-\input{sections/Methods}
+\input{sections/RelatedWork}
+\input{sections/DesignedMethodology}
+\input{sections/SystemImplementation}
 \input{sections/Results}
 \input{sections/Conclusion}
+%\input{sections/Acknowledgment}
 

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Conclusion.tex
01.08.21.1

@@
-\section{Conclusions}
-The designed NLP-based methodology digitizes the roaming agreement by classifying the sub-articles of the roaming agreement as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
-The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy  determination  based  on  a  simple  inspection  at sub-article level determines for the first sample roaming agreement, an accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and an accuracy of 80\% in the classification of \textit{customized texts}.
-These results are improved for the second sample roaming agreement with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}.
+\section{Conclusions}\label{conclusions}
+The designed NLP-based methodology presented in this paper digitizes the RA by accurately extracting its contents and classifying its sub-articles as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
+The test phase allows to evaluate the results obtained from two types of experiments conducted to measure the accuracy to establish that on the one hand, the accuracy determination based on a simple inspection at sub-article level determines for the first sample roaming agreement, and accuracy of 80.9\% in the classification of \textit{standard clauses}, an accuracy of 82.9\% in the classification of \textit{variations} and accuracy of 80\% in the classification of \textit{customized texts}.
+These results are improved for the second sample RA with an accuracy of 92.9\% in the classification of \textit{standard clauses}, an accuracy of 87.5\% in the classification of \textit{variations} and an accuracy of 91.2\% in the classification of \textit{custom texts}.
 On the other hand, the determination of the accuracy based on the comparison of symbols determines for the first roaming agreement sample, an accuracy of 84.7\% of the total of 72 analyzed sub-articles with a common percentage of favorable symbols.
@@
 Therefore, the results demonstrate the feasibility of applying the proposed methodology.
-As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other similarity classes, e.g., cosine similarity in order to improve the results obtained.
+As part of a process of continuous improvement of the designed methodology within future research lines we aim to conduct other accuracy tests applying other text similarity types, such as cosine similarity, to improve the results obtained.
 
-The proposed NLP Engine constitutes a part of a project that has as main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development and evaluation of the rest of the sub-systems that mainly include the smart contracts that automate the negotiation process, as well as the integration with the developed NLP Engine.
+The proposed NLP Engine constitutes a part of a project that has as the main objective of transforming the current Telecommunication Roaming Agreement drafting and negotiation process into a digitalized version based on the transparency promoted by blockchain technology, future research works include the design, development, and evaluation of the rest of the sub-systems that mainly include the smart contracts that automate the negotiation process, as well as the integration with the developed NLP Engine.

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/DesignedMethodology.tex
01.08.21.1

\section{NLP Engine methodology}\label{methodology}
In general, our design consists of the following two approaches (which we discuss in more detail in this section): \textit{detection} and \textit{comparison}. While \textit{detection} has symbols as basic processing unit, \textit{comparison} has sub-articles as basic processing unit. \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the RA. For this purpose, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content of text documents by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.

\textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the RA concerning the sub-articles present in the GSMA standard template. In this regard, \textit{text similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering, and information retrieval problems \cite{7429408}. We employ \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}. As a result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the RA) represents a \textit{customized text}. Thus, the intermediate case is represented by the \textit{variation} in which there is a high coincidence between sub-articles, and the existing differences are given by the presence of \textit{variables} such as the commercial names of MNOs and the start date of the RA. The next section integrates tools, NLP techniques, and text processing techniques as part of the designed methodology.

\subsection{Designed Methodology}
The flow chart in Fig.~\ref{fig1} is a general scheme of the methodology designed for the NLP Engine, which will be explained in detail below.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.4\textwidth]{images/methodology.png}}
\caption{Overview of the designed methodology.}
\label{fig1}
\end{figure}

The starting point of the methodology is the decompression and content extraction of PDF files (each PDF file contains a RA). The file name is used as one of the identifiers of the output file. The next step is to find similarities in document texts so that headers and footers are detected to avoid undesired characters. For that purpose, the mechanism used is the detection of different font sizes and weights. Once the PDF format has been converted to text, headers, and footers as well as undesired characters are removed. It is now possible to perform both \textit{detection} and \textit{comparison}.

The \textit{detection} phase includes a requirement associated with the Amazon Comprehend tool regarding the number of symbols to be sent via REST API. For this reason, the text is segmented into pieces of 100 symbols. For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format \cite{AWS2021}, which must be grouped and further processed. The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'. In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field. Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree. The designed logic is particularized according to the type of \textit{variable} to be detected. For instance, for the name of the MNO, the 'Score', 'Frequency', and 'BeginOffset' are prioritized, in addition to verifying the number of occurrences within the key phrases. The detected \textit{variables} are stored to be used later to determine which ones are part of the \textit{variations} or \textit{customized texts}.

The \textit{comparison} phase implies to separate by articles and then by sub-articles. Since several of the possibilities of article names are loading in the NLP Engine is easy to locate the corresponding article in the GSMA standard template and therefore, to establish comparisons at the sub-article level. \textit{Jaccard's similarity} associates a score to the sub-article ID. Thus, a sub-article is considered a \textit{standard clause} whether the score assigned is greater than 0.85 (score $\geq$ 0.85). In addition, a sub-article is considered a \textit{custom text} whether the score assigned is less than 0.15 (score $\leq$ 0.15). Finally, a sub-article is considered a \textit{variation} whether the score assigned is between 0.85 and 0.15 (0.15 $<$ score $<$ 0.85). At this point, the NLP Engine is ready to populate the output file, inspecting in case of to have tagged the sub-articles as \textit{variation} or \textit{customized texts}, the \textit{variables} that it contains.

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
01.08.21.1

@@
-\section{Introduction}
+\section{Introduction}\label{intro}
 The roaming service maintains the persistent connectivity of subscribers in different networks and locations.
-Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{Tanaka2013}.
+Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN) when roaming outside the coverage range of the HPMN \cite{Tanaka2013}.
 However, before ensuring persistent connectivity in VPMN the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).
 In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
-The testing and implementation phases are straight forward as they are related with implementing what is agreed on the drafting phase.
-However, the drafting phase is ambiguous and involves multiple iterations of exchange of draft text and proposed articles between both parties, i.e.
+On the one hand, the testing and implementation phases are straightforward as they are focused on implementing what is agreed on the \textit{drafting} phase.
+On the other hand, the \textit{drafting} phase is ambiguous and involves multiple iterations of the exchange of draft text and proposed articles between both parties, i.e.
 the MNOs.
 
-Therefore, in order to reduce the exerted efforts and standardize the technical, commercial and legal aspects of the RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
+Therefore, to reduce the exerted efforts and standardize the technical, commercial and legal aspects of the RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{Ferwerda2018}.
 In addition, many organizations attempt to unify RAs.
-For example, Rocco\footnote{Rocco Group: https://www.rocco.group}, which is a company specialized in telecommunication reports including roaming agreements, provides a list of the most commonly used GSMA standards.
+For example, Rocco\footnote{Rocco Group: https://www.rocco.group}, which is a company specialized in telecommunication reports including RAs, provides a list of the most commonly used GSMA standards.
 It summarizes these standards as follows \cite{ROCCO2017}: (1) AA.12 constitutes the permanent reference document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.) and (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.).
 
-While it is true that it is not mandatory to follow the standards proposed by the GSMA organization, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{ROCCO2017a}.
-Therefore, the first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards.
-Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates.
-This necessitates discretizing the bulk of the roaming agreement template and classifying each word/clause from an existing classes as follows:
+While it is true that it is not mandatory to follow the standards proposed by the GSMA organization, according to authoritative voices in the field of negotiating RA \textit{drafting}, most MNOs follow them strictly \cite{ROCCO2017a}.
+Therefore, the first point to consider in the RA \textit{drafting} is how far it has deviated from the GSMA's proposed standards.
+Thus, during the \textit{drafting} process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates.
+This necessitates discretizing the bulk of the RA template and classifying each word/clause into existing classes as follows:
 
@@
 However, the \textit{drafting} of a RA goes through a complex negotiation process in which, at present, the parties still use asynchronous flows such as e-mail or even regular mail to exchange the information.
-Thus, this traditional negotiation process has multiple drawbacks including lacks of transparency, which can lead to violations of the RA by MNOs.
-In addition, this process is laborious and time consuming.
+Thus, this traditional negotiation process has multiple drawbacks including lack of transparency, which can lead to violations of the RA by MNOs.
+In addition, this process is laborious and time-consuming.
 As experts point out, the entire process can take up to one month, depending on the responsiveness of the MNOs \cite{ROCCO2017a}.
-Therefore, it is necessary to provide a transparent digitalization system for RA drafting negotiations, which guarantees transparency and shortening the negotiation time, which guarantees transparency and shortening the negotiation time, which could be in days or even weeks.
-Hence, this work develops a framework that exploits the advancement in the Natural Language Processing (NLP) discipline and use it as a legal text in the digitalization engine.
-This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent drafting of Roaming Agreements.
-The proposed NLP Engine analyzes articles and sub-articles of the RA by determining the existence of variables, variations, standard clauses and customized texts.
-To do so, the proposed NLP Engine relies on the advancement of NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) in drafting RAs.
+Therefore, it is necessary to provide a transparent digitalization system for RA \textit{drafting} negotiations, which guarantees transparency and shortening the negotiation time, which could be in days or even weeks.
+Hence, this work develops a framework that exploits the advancement in the Natural Language Processing (NLP) discipline and uses it as an engine to digitalize legal text.
+This NLP Engine constitutes the starting point for the digitalization of the negotiation process towards a transparent \textit{drafting} of RAs.
+The proposed NLP Engine analyzes articles and sub-articles of RAs by determining the existence of \textit{variables}, \textit{variations}, \textit{standard clauses} and \textit{customized texts}.
+To do so, the proposed NLP Engine relies on multiple NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) tagging in the \textit{drafting} of RAs.
+
+%{\color{red}ADD: list of contributions. The main contributions of this work can be summarized in the following points: (1) .... (2) ....}
+
+%{\color{red}The remainder of this paper is organised as follows: we briefly review existing work in Section~\ref{existing}, we describe our methods in details in Section~\ref{methods}, we then present and discuss our results in Section~\ref{results}, followed by conclusions and ideas for future work in the last section.}
 

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/RelatedWork.tex
01.08.21.1

\section{Related work}\label{related}

The existing work that is related to the RAs can be categorized into two main categories. The first category encompasses the work, which focused on transparent digitalization of RAs~\cite{9369516, 9024541, Huillet2020}, whereas the second category includes the works that apply existing NLP techniques-based text processing systems~\cite{8487847, 9138070, 9104105}.

Both in the scientific literature and business environments, there are important approaches to RA digitalization. Thus, the work discussed in~\cite{9369516} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. Despite the contributions of this work in the RA \textit{implementation} phase, the fact of performing the implementation on the Ethereum network implies that the participating MNOs will bear the high cost of gas fees for the transactions. Additionally, although the authors justify the latency given that they repeated the experiment 100 times, the proof of work nature of the network implies drafting actions are likely to suffer congestion anytime. A second approach focuses uniquely on the billing of the services obtained as a result of the RA is reported in~\cite{9024541}. This agreement is incorporated as part of a chaincode of a Hyperledger Fabric Blockchain (HFB) network so the work contributes significantly to the digitalization process of the RA, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. Although this work also constitutes an important contribution regarding the use of HFB in the field of telecommunications to address problems around Managing RAs, Inter-carrier Settlements, and Mobile Number Portability, its approach is one of review and proposal, however, it lacks an implementation section that would allow demonstrating the feasibility of the proposals. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom, and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties~\cite{Huillet2020}. This proposal is also of considerable value in the business environment, however, its focus relates only to the \textit{implementation} phase of the RA and not to the \textit{drafting} phase.

Additionally, the scientific literature addresses text processing systems based on NLP techniques in domains such as the judiciary. Thus, the approach introduced in~\cite{8487847} addresses the process of digitalization in the judicial sectors from archives of judicial records for which the authors have designed a text analysis tool that includes grammatical analysis of documents in English based on NLP techniques. The proposed article also constitutes an important contribution in terms of the design of the linguistic analysis based on NLP techniques. However, it lacks formal evaluation in terms of accuracy of NLP implementation. In addition, the work reported in~\cite{9138070} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied. Finally, authors of~\cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although the value of the contribution lies in the use of NLP techniques from the Amazon Comprehend tool, the paper lacks a formal results section, therefore it is difficult to determine the accuracy of the proposed tool.

Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the RA. Therefore, and to the best of our knowledge, we can affirm that our work introduces a topic with a high degree of novelty.

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Results.tex
01.08.21.1

@@
-\section{Discussion of Results}
-Since PDF, i.e., input files of the NLP Engine architecture consist of unstructured text and for instance, undesired characters may remain despite text parsing, it is mandatory determine the \textit{accuracy} of the results obtained once the output JSON file has been populated.
+\section{Discussion of Results}\label{results}
+Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text.
+Because of this, undesired characters may remain despite text parsing.
+Therefore, it is mandatory to determine the \textit{accuracy} of the results obtained once the output JSON file has been populated.
 For this purpose, two types of experiments have been conducted to determine the \textit{accuracy} of the results.
-On the one hand, a simple inspection at sub-article level and on the other hand, a verification based on symbol comparison.
-The tests are performed on two Roaming Agreements sample of the MNOs Proximus and Orange \cite{proximus}.
+On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison.
+The tests were performed on two RA samples of the MNOs Proximus and Orange \cite{proximus}.
 Each experiment is described below and the results obtained are discussed in the same section.
@@
 \subsection{Accuracy determination based on a simple inspection at sub-article level}
-The first accuracy analysis consists of determining by simple inspection, i.e., human-eye inspection, whether each sub-article of the roaming agreement constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} with respect to the GSMA standard template.
+The first accuracy analysis consists of visually determining, i.e., human-eye inspection, whether each sub-article of the RA constitutes a \textit{variation}, a \textit{standard clause} or a \textit{customized text} concerning the GSMA standard template.
 The results obtained are then compared with the values populated in the NLP Engine output file, for the same sub-article.
-Considering that the results obtained from the simple inspection constitute the observations and the values collected from sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample roaming agreements.
-In this regard, the confusion matrix in the Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
-Proof of this is the fact that the main diagonal of the matrix concentrates the highest number of True Positives.
+Considering that the results obtained from the simple inspection constitute the observations and the values collected from the sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample RA.
+In this regard, the confusion matrix in Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
+Proof of this is the fact that the main diagonal of the matrix contains the highest number of True Positives.
 Table~\ref{table3} summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
@@
 
-The Table~\ref{table2}, as well as Table~\ref{table1}, shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine classifies properly the sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Orange sample roaming agreement.
-Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} concentrates the highest number of True Positive.
+Table ~\ref{table2} shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine correctly classifies the sub-articles as \textit{standard clauses}, \textit{variations}, or \textit{customized texts} for the Orange sample RA.
+Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} has the highest number of True Positive.
 Table~\ref{table3} also summarizes the accuracy of the NLP Engine's sub-article classification capability in percentage terms as \textit{standard clauses}, \textit{variations} and \textit{customized texts}.
@@
 
-Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document with respect to another.
+Beyond the fact that the results themselves can be considered as acceptable, the other behavior to be highlighted in Table~\ref{table3} is the greater classification capacity into \textit{standard clauses}, \textit{variations} and \textit{customized texts} of the NLP Engine in one document concerning another.
 
 \subsection{Accuracy determination based on symbol comparison}
-The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file with respect to the sub-articles existing in the input file containing the Roaming Agreements.
+The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file concerning the sub-articles existing in the input file containing the RAs.
 This comparison is performed at the symbol level, considering the order of appearance of each symbol.
-For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used manually copying sub-article by sub-article.
-For each sub-article is determined:
+For that purpose, the text comparison tool Countwordsfree (\cite{countwordsfree}) is used by manually copying sub-article by sub-article.
+For each sub-article, the following values are determined:
 
@@
 
-The following radar chart allow us to analyze the results for each roaming agreement.
-The radar chart contain in the inner radius the Common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article.
-Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample roaming agreement.
-The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when output file was populated.
+The illustrated radar charts allow us to analyze the results for each RA.
+The radar chart contains in the inner radius the common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article.
+Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample RA.
+The conclusion that can be reached by simple inspection is that only 11 of the 72, i.e.,  84.7\% of the analyzed sub-articles are affected, mostly by the introduction of undesired characters when the output file was populated.
 
-Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample roaming agreement.
-In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample roaming agreement.
+Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample RA.
+In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample RA.
+
+%\subsection{Analysis of the novelty of the contribution}
+
+%\begin{table}[htbp]
+%\caption{Analysis of the novelty of the contribution.}
+%\begin{center}
+%\begin{tabular}{|c|c|c|c|c|c|c|c|}
+%\hline
+%\multirow{2}{*}{\textbf{Field}} & %\multirow{2}{*}{\textbf{C}} & %\multicolumn{3}{c|}{\textbf{RA phase}} & %\multicolumn{3}{c|}{\textbf{NLP  Engine}} \\ %\cline{3-8} 
+%&  & Dr & I & T & D & I & T \\ \hline
+%\textbf{} & our contribution &  &  &  &  & &  \\ %\hline
+%\multirow{3}{*}{\textbf{RA}} 
+%& \cite{9369516} &  &  &  &  &  &  \\ \cline{2-8} 
+%& \cite{9024541} &  &  &  &  &  &  \\ \cline{2-8} 
+%& \cite{Huillet2020} &  &  &  &  &  &  \\ \hline
+%\multirow{3}{*}{\textbf{NLP}} 
+%& \cite{8487847} &  &  &  &  &  &  \\ \cline{2-8} 
+%& \cite{9138070} &  &  &  &  &  &  \\ \cline{2-8} 
+%& \cite{9104105} &  &  &  &  &  &  \\ \hline
+%\end{tabular}
+%\label{table3}
+%\end{center}
+%\end{table}

### 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/SystemImplemetation.tex
01.08.21.1

\section{System Implementation}\label{implementation}
Fig.~\ref{fig2} shows the overall architecture of the NLP engine integrated into a docker infrastructure that includes three parts. The input files include the RA text file as well as the GSMA standard templates. The processing layer includes the logic associated with the NLP engine, i.e. the implementation of the designed methodology. The output file constitutes a JSON file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}. In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.20\textwidth]{images/NLP_Engine.png}}
\caption{NLP Engine overall architecture.}
\label{fig2}
\end{figure}

The input and output files are accessed by the container through Docker volumes. In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point. Although the NLP Engine constitutes a library, it must in turn, integrate other libraries, among which boto3 \cite{boto3}. Boto3 is a Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS). The NLP Engine imports the specific service associated with Amazon Comprehend. PyMuPDF (\cite{PyMuPDF}) constitutes another library imported into the NLP Engine to be used for headers and footers detection. Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library but must also install the libraries it imports. The \textit{similarity} has been implemented in a pluggable way, therefore at code level, it is easy to change the \textit{Jaccard's similarity} for another one, e.g., cosine similarity \cite{Gupta2018}.

%\textcolor{red}{add link to github repo containing the full python code at some point?}

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/DesignedMethodology.tex
01.08.21.4

@@
 For that purpose, the mechanism used is the detection of different font sizes and weights.
-Once the PDF format has been converted to text, headers, and footers as well as undesired characters are removed.
+Once the PDF format has been converted to text is removed headers, and footers, as well as undesired characters (e.g., spaces, end-lines), in what is a parsing step.
 It is now possible to perform both \textit{detection} and \textit{comparison}.
@@
 The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'.
-In turn, it adds to these the 'Frequency' field that stores the number of repetitions of the entity stored in the 'Text' field.
+In turn, it adds to these the 'Frequency' field that indicates the number of repetitions of entities with same the same name, i.e., the same 'Text' field.
 Once this filtering has been done, entities are sorted according to a logic that defines their relevance degree.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
01.08.21.4

@@
 In this regard, it is possible to establish three stages within the RA: \textit{drafting}, \textit{testing} and \textit{implementation}.
-On the one hand, the testing and implementation phases are straightforward as they are focused on implementing what is agreed on the \textit{drafting} phase.
+On the one hand, the \textit{testing} and \textit{implementation} phases are straightforward as they are focused on implementing what is agreed on the \textit{drafting} phase.
 On the other hand, the \textit{drafting} phase is ambiguous and involves multiple iterations of the exchange of draft text and proposed articles between both parties, i.e.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/RelatedWork.tex
01.08.21.4

@@
 The work constitutes a valuable contribution in terms of design and implementation of the tool, however, it lacks demonstration of the feasibility of use, as well as determination of the accuracy of the NLP techniques applied.
-Finally, authors of~\cite{9104105} propose a model for implementing sentimental analysis using Amazon Comprehend.
+Finally, authors of~\cite{9104105} propose a methodology for implementing sentimental analysis using Amazon Comprehend.
 This system performs an audio-to-text transcription and then performs the processing of the obtained text.
@@
 
-Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunication field and even less in the context of a transparent digitalization of the RA.
+Although these studies constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecommunications field and even less in the context of a transparent digitalization of the RA.
 Therefore, and to the best of our knowledge, we can affirm that our work introduces a topic with a high degree of novelty.

### 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Results.tex
01.08.21.4

@@
 On the one hand, a simple inspection at the sub-article level and on the other hand, a verification based on symbol comparison.
-The tests were performed on two RA samples of the MNOs Proximus and Orange \cite{proximus}.
+The tests have been performed on two real RA samples from the mobile operators Proximus and Orange \cite{proximus}.
 Each experiment is described below and the results obtained are discussed in the same section.
@@
 Considering that the results obtained from the simple inspection constitute the observations and the values collected from the sub-articles classification file constitute the predicted values, the following confusion matrices allow us to analyze the results for each sample RA.
-In this regard, the confusion matrix in Table~\ref{table1} indicates that the \textit{accuracy} at which the 72 sub-articles analyzed are satisfactorily classified by the NLP Engine as \textit{standard clauses}, \textit{variations} or \textit{customized texts} is acceptable.
+In this regard, the confusion matrix in Table~\ref{table1}  shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the accuracy at which the NLP Engine correctly classifies 61 of 72 analyzed sub-articles as \textit{standard clauses}, \textit{variations} or \textit{customized texts} for the Proximus sample RA.
 Proof of this is the fact that the main diagonal of the matrix contains the highest number of True Positives.
@@
 
-Table ~\ref{table2} shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine correctly classifies the sub-articles as \textit{standard clauses}, \textit{variations}, or \textit{customized texts} for the Orange sample RA.
+Table~\ref{table2} shows satisfactory results for the NLP Engine's predictive capability, i.e., regarding the \textit{accuracy} at which the NLP Engine correctly classifies 79 of the 86 sub-articles as \textit{standard clauses}, \textit{variations}, or \textit{customized texts} for the Orange sample RA.
 Using the same evaluation criteria, it is observed how the main diagonal of the confusion matrix in Table~\ref{table2} has the highest number of True Positive.
@@
 \subsection{Accuracy determination based on symbol comparison}
-The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file concerning the sub-articles existing in the input file containing the RAs.
+The second accuracy analysis involves establishing a comparison between the sub-articles populated in the output file concerning the sub-articles existing in the input file containing the real RAs.
 This comparison is performed at the symbol level, considering the order of appearance of each symbol.
@@
 The illustrated radar charts allow us to analyze the results for each RA.
-The radar chart contains in the inner radius the common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article.
+The radar chart contains in the inner radius the common percentage of symbols between compared sub-articles and in the outer radius the identifier of the compared sub-article, i.e., the sub-articles contained in the output file.
 Fig.~\ref{fig3} shows a comparison in terms of the common percentage of symbols between compared sub-articles for the Proximus sample RA.
@@
 Similarly, Fig.~\ref{fig4} shows a comparison in terms of the common percentage of symbols between the sub-articles compared for the Orange sample RA.
-In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained for the Proximus sample RA.
+In this case, only 7 of the 86, i.e., 91.9\% of the analyzed sub-articles are affected by the introduction of undesired characters when the output file is populated, thus improving the results obtained regarding the RA Proximus sample.
 

### 2021-09-05 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/DesignedMethodology.tex
05.08.21.1

@@
-\section{NLP Engine methodology}\label{methodology}
+\section{NLP Engine methodology}\label{sec:methodology}
 In general, our design consists of the following two approaches (which we discuss in more detail in this section): \textit{detection} and \textit{comparison}.
@@
 \textit{Detection} represents the capability to detect \textit{variables} in a text file, i.e., the RA.
-For this purpose, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content of text documents by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text \cite{AWS2021}.
+For this purpose, \textit{Amazon Comprehend} constitutes the enabling technology of the \textit{detection} approach, since it is a service that uses NLP techniques to extract insights about the content of text documents by recognizing  the  entities,  key  phrases,  language,  sentiments,  and  other  common  elements  in  a  text~\cite{AWS2021}.
 
 \textit{Comparison} represents the capability to find \textit{similarities} and differences between the sub-articles present in the RA concerning the sub-articles present in the GSMA standard template.
-In this regard, \textit{text similarity} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering, and information retrieval problems \cite{7429408}.
-We employ \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets \cite{Gupta2018}.
+In this regard, \textit{text similarity}~\cite{Deza2009} constitutes the enabling technology of the \textit{comparison} approach, since it is a resource commonly used for pattern classification, clustering, and information retrieval problems~\cite{7429408}.
+We employ \textit{Jaccard's similarity} which is defined as the size of the intersection divided by the size of the union of two sets~\cite{Gupta2018}.
 As a result of the \textit{comparison}, it is determined that while an almost total coincidence between texts at the sub-article level represents a \textit{standard clause}, an almost null coincidence between texts (or simply the non-existence of a sub-article of the GSMA standard template in the RA) represents a \textit{customized text}.
@@
 For this reason, the text is segmented into pieces of 100 symbols.
-For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format \cite{AWS2021}, which must be grouped and further processed.
+For each symbol chunk the API outputs entities, key phrases and sentiment in JavaScript Object Notation (JSON) format~\cite{AWS2021}, which must be grouped and further processed.
 The designed logic collects the most important fields such as: 'BeginOffset', 'EndOffset', 'Score', 'Text', 'Type', 'PartOfSpeech', and 'Tag'.

### 2021-09-05 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Introduction.tex
05.08.21.1

@@
 
-%{\color{red}The remainder of this paper is organised as follows: we briefly review existing work in Section~\ref{existing}, we describe our methods in details in Section~\ref{methods}, we then present and discuss our results in Section~\ref{results}, followed by conclusions and ideas for future work in the last section.}
+\textcolor{blue}{The remainder of this paper is organised as follows: we briefly review existing work in Section~\ref{sec:related}, we describe our methods in details in Section~\ref{sec:methodology}, we then present and discuss our results in Section~\ref{sec:results}, followed by conclusions and ideas for future work in the last section.}
 

### 2022-06-25 A_Natural_Language_Processing_Approach_for_the_Digitalization_of_Roaming_Agreements/sections/Results.tex
25.06.22

--- 2021-09-02 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/Results.tex
@@
-\section{Discussion of Results}\label{results}
+\section{Discussion of Results}\label{sec:results}
 Our NLP Engine architecture receives PDF files as inputs, and PDF files normally consist of unstructured text.

### 2022-06-25 ILCICT_2022/paper-LaTex/sections/SystemImplemetation.tex
25.06.22

--- 2021-09-01 A methodological framework to enable the roaming agreement digitalization: An NLP-based approach/sections/SystemImplemetation.tex
@@
 The input files include the RA text file as well as the GSMA standard templates.
-The processing layer includes the logic associated with the NLP engine, i.e.
-the implementation of the designed methodology.
-The output file constitutes a JSON file populated with the classification of articles and sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
+The processing layer includes the logic associated with the NLP engine, i.e., the implementation of the designed methodology.
+The output file constitutes a JSON file populated with the classification of sub-articles as \textit{standard clauses}, \textit{customized texts} and \textit{variations}.
 In addition, each article includes the set of \textit{variables} it contains and each sub-article contains the specific \textit{variable} detected as long as it has been classified as \textit{variation} or \textit{customized texts}.
@@
 In addition, the NLP Engine has been developed as a Python v3.8 based library and therefore must be imported and run from an entry point.
-Although the NLP Engine constitutes a library, it must in turn, integrate other libraries, among which boto3 \cite{boto3}.
+Although the NLP Engine constitutes a library, it must in turn, integrate other libraries such as boto3 (\cite{boto3}) and PyMuPDF (\cite{PyMuPDF}).
 Boto3 is a Software Development Kit (SDK) for Python, created and supported by Amazon Web Services (AWS).
 The NLP Engine imports the specific service associated with Amazon Comprehend.
-PyMuPDF (\cite{PyMuPDF}) constitutes another library imported into the NLP Engine to be used for headers and footers detection.
+PyMuPDF constitutes another library imported into the NLP Engine to be used for headers and footers detection.
 Therefore, the docker image built for the NLP Engine must not only install the NLP Engine library but must also install the libraries it imports.
